---
title: "bggm-var-investigation"
author: "Björn Siepe"
date: "2022-11-18"
output: html_document
---
In this file, I investigate some of the properties of BGGM var_estimate. 
Does it actually work well? If so, the following should be true.
1. It should perform regularization as it says.
2. It should recover roughly the same estimate as, e.g., graphicalVAR. 


```{r}
source("aux_funs.R")
```



# Test regularization
```{r}
# library("BGGM", lib.loc = "C:/Users/Bjoern/R-dev")


set.seed(2022)
compgraph <- graphicalVAR::randomGVARmodel(Nvar = 6, probKappaEdge = 0.4, probBetaEdge = .2)
dat <- as.data.frame(graphicalVAR::graphicalVARsim(200, beta = compgraph$beta, kappa = compgraph$kappa))
res <- var_estimate(dat,
                          beta_sd = 1)
res2 <- BGGM::var_estimate(dat,
                           beta_sd = 0.1)


# Try the same for rho
res3 <- BGGM::var_estimate(dat,
                          rho_sd = 0.5)
res4 <- BGGM::var_estimate(dat,
                          rho_sd = 0.05)



```

# Compare with GraphicalVAR

For now, just simulate 100 datasets from the same DGP. 
```{r generate-data}
# Storage
l_gvardata <- list()

# Simulation conditions
n_ind <- 200   # number of individuals (so models to create)
n_tp <- 150     # number of timepoints per time series

ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)

l_gvardata <- sim_raw_parallel(dgp = compgraph, n = n_ind, 
                                tp = n_tp, means = 0,
                                standardize = TRUE)

stopCluster(cl)





```

```{r fit-models}
# Model specifics
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000

l_compres <- list()
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)

l_compres$bggm <- fit_var_parallel(data = l_gvardata, n = n_ind,
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
                 iterations = n_iter)

l_compres$gvar <- foreach(i = seq(n_ind), .packages = "graphicalVAR") %dopar% {
  tmp_res <- graphicalVAR(data = l_gvardata[[i]]$data, 
               lambda_beta = 0,
               lambda_kappa = 0, 
               scale = TRUE, 
               gamma = 0)
  
  tmp_res
  
}

stopCluster(cl)


```



Now we can compare the results. What do we look at? Due to no regularization, do not look at true positives/false positives here. 
- difference from data-generating process


TODO: Is it fine not to look at the intercepts? This might be important. 
TODO: Do I need the transpose?
TODO: Add correlations


```{r compare-results}
comp_res <- compare_dgp(true = compgraph, 
                        est_bggm = l_compres$bggm, 
                        est_gvar = l_compres$gvar, n = 200)


```

Plot results: (this should be added as a function later on)
```{r plot-results}



```


Works pretty well for n = 200 and one graph. Default priors seem to be okay, only has convergence issues in some cases.  





# Simulation study

## Data Generation
Just use "truegraph" data from main simulation study for now. 
TODO: Download this from the server. 
```{r}
l_raw <- readRDS(here::here("output/l_raw.RDS"))
l_graphs <- readRDS(here::here("data/l_graphs.RDS"))

# Only truegraph
l_dgp <- list()
l_dgp$graph1 <- lapply(l_raw$graph1, function(x){
  y <- x$truegraph
  y
})
l_dgp$graph2 <- lapply(l_raw$graph2, function(x){
  y <- x$truegraph
  y
})
l_dgp$graph3 <- lapply(l_raw$graph3, function(x){
  y <- x$truegraph
  y
})




```



## Estimation
Estimate both graphicalVAR in default settings as well as BGGM with varying priors.
```{r}
# Priors
dgp_names <- c("graph1", "graph2", "graph3")
dgp <- c(1,2,3)
rho_sd <- c(0.1, 0.3, 0.5)
beta_sd <- c(0.2, 0.5, 1)
n_tp <- c(50, 100, 200, 400, 1000) 
tp_cond <- c(1,2,3,4,5)   # different tp conditions

cond_grid <- expand.grid(dgp = dgp,
                         n_tp = tp_cond,
                         rho_prior = rho_sd, 
                         beta_prior = beta_sd)
n_iter <- 50000
seed <- 2022
set.seed(seed)



# Estimating for each model 
# store BGGM results under "nonselect"
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
clusterExport(cl = cl, "summarize_post")
registerDoParallel(cl)
l_res <- list()


# TODO maybe actually use save_files to save results to disc
# Need to adopt such that select works together with summarize_post

for(n in 1:nrow(cond_grid)) {
  dgp_ind <- as.numeric(cond_grid[n, "dgp"])
  tp_ind <- as.numeric(cond_grid[n, "n_tp"])
  r_sd <- as.numeric(cond_grid[n, "rho_prior"])
  b_sd <- as.numeric(cond_grid[n, "beta_prior"])
  print(paste0(nrow(cond_grid)-n, " to go!"))
  l_res[[n]]  <- fit_var_parallel_merged(l_dgp[[dgp_ind]][[tp_ind]],
                          rho_prior = r_sd,
                          beta_prior = b_sd,
                          iterations = n_iter,
                          n = 100,
                          nds = 100,
                          seed = seed,
                          summarize_post = TRUE,
                          cred_int = c(0.9, 0.95, 0.99),
                          pruneresults = FALSE,
                          save_files = FALSE,
                          multigroup = FALSE,
                          select = TRUE)
    

  
}
stopCluster(cl)

# saveRDS(l_res, here::here("output/bggm-var-sim-res.Rds"))
l_res_bggm <- readRDS(here::here("output/bggm-var-sim-res.Rds"))


# Attach the simulation conditions
for(m in 1:nrow(cond_grid)){
  for(i in 1:length(l_res_bggm[[m]])){
    l_res_bggm[[m]][[i]]$sim_cond <- cond_grid[m,]
  }
}

```
### Fit graphicalVAR
```{r}
# Conditions of varying sparsity
dgp_names <- c("graph1", "graph2", "graph3")
dgp <- c(1,2,3)
gamma_ebic <- c(0, 0.5)      # EBIC hyperparamater
lambda <- c(NA, 0)
n_tp <- c(50, 100, 200, 400, 1000) 
tp_cond <- c(1,2,3,4,5)   # different tp conditions

cond_grid_gvar <- expand.grid(dgp = dgp,
                         n_tp = tp_cond,
                         gamma_ebic = gamma_ebic,
                         lambda = lambda)




ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
clusterExport(cl = cl, "fit_graphicalvar_parallel")
registerDoParallel(cl)
l_res_gvar <- list()
time_before_gvar <- Sys.time()
for(n in 1:nrow(cond_grid)) {
  dgp_ind <- as.numeric(cond_grid_gvar[n, "dgp"])
  tp_ind <- as.numeric(cond_grid_gvar[n, "n_tp"])
  gamma_ebic <- as.numeric(cond_grid_gvar[n, "gamma_ebic"])
  lambda <- as.numeric(cond_grid_gvar[n, "lambda"])
  print(paste0(nrow(cond_grid_gvar)-n, " to go!"))
  
  # unregularized
  if(!is.na(lambda)){
   l_res_gvar[[n]]  <- fit_graphicalvar_parallel(l_dgp[[dgp_ind]][[tp_ind]],
                                                  n = 100,
                                                  gamma = gamma_ebic,
                                                  nLambda = 50, 
                                                  pruneresults = TRUE, 
                                                  lambda_beta = lambda,
                                                  lambda_kappa = lambda)
                            
  }
  # regularized
  if(is.na(lambda)){
   l_res_gvar[[n]]  <- fit_graphicalvar_parallel(l_dgp[[dgp_ind]][[tp_ind]],
                                                 n = 100,
                                                 gamma = gamma_ebic,
                                                 nLambda = 50, 
                                                 pruneresults = TRUE)
    
  }
    

  
}
stopCluster(cl)

time_after_gvar <- Sys.time() - time_before_gvar
# saveRDS(l_res_gvar, here::here("output/graphicalvar-sim-res.Rds"))
l_res_gvar <- readRDS(here::here("output/graphicalvar-sim-res.Rds"))


 
# Attach the simulation conditions
for(m in 1:nrow(cond_grid_gvar)){
  for(i in 1:length(l_res_gvar[[m]])){
    l_res_gvar[[m]][[i]]$sim_cond <- cond_grid_gvar[m,]
  }
}
    








```




## Evaluation
Evaluate both with and without graph selection.

Evaluation function
```{r}
# TODO be very careful about transposing beta here or not!!!!

bias <- function(e,t){
  b <- mean(abs(e - t), na.rm = TRUE)
}


eval_bggm <- function(fit,
                      cred_int = c(0.9, 0.95, 0.99),    # different credible intervals
                      nds = 100,         # number of datasets per simulation condition
                      dgp_list = l_graphs){
  
  
  # Prepare output
  l_out <- list()
  
  
  # Save arguments
  args <- fit$args
  l_out$dgp_ind <- fit$sim_cond$dgp
  l_out$tp_ind <- fit$sim_cond$n_tp
  l_out$rho_prior <- fit$sim_cond$rho_prior
  l_out$beta_prior <- fit$sim_cond$beta_prior
  
  
  ## Find corresponding true graph
  true_graph <- l_graphs[[l_out$dgp_ind]]
  beta_true <- true_graph$beta
  kappa_true <- true_graph$kappa
  
  # Calculate PCOR 
  # TODO doublecheck this
  pcor_true <- -1*stats::cov2cor(kappa_true)
  
  
  #--- Nonselect Method ---#
  # Point estimates
  beta_est <- fit$beta_mu
  pcor_est <- fit$pcor_mu
  
  
  # Compute Bias
  l_out$bias_beta <- bias(beta_est, beta_true)
  l_out$bias_pcor <- bias(pcor_est, pcor_true)
  
  # Correlations
  # TODO should I do it like this? just ignore matrix structure?
  l_out$cor_beta <- cor(c(beta_est), c(beta_true))
  l_out$cor_pcor <- cor(c(pcor_est), c(pcor_true))
  
  
  
  #--- Select Method ---#
  # Obtain different credible intervals
  cred_interval <- fit$cred_interval
  
  
  # Obtain estimates with selection
  beta_est_sel <- fit$beta_weighted_adj
  pcor_est_sel <- fit$pcor_weighted_adj
  
  ## Bias
  l_out$bias_beta_sel <- bias(beta_est_sel, beta_true)
  l_out$bias_pcor_sel <- bias(pcor_est_sel, pcor_true)
  
  ## True/False Positive/Negative
  # TP
  l_out$true_pos_beta <- sum(beta_true != 0 & beta_est_sel != 0)
  l_out$true_pos_pcor <- sum(pcor_true != 0 & pcor_est_sel != 0)
  
  # FP
  l_out$fal_pos_beta <- sum(beta_true == 0 & beta_est_sel != 0)
  l_out$fal_pos_pcor <- sum(pcor_true == 0 & pcor_est_sel != 0)  
  
  # TN
  l_out$true_neg_beta <- sum(beta_true == 0 & beta_est_sel == 0)
  l_out$true_neg_pcor <- sum(pcor_true == 0 & pcor_est_sel == 0)
  
  # FN
  l_out$fal_neg_beta <- sum(beta_true != 0 & beta_est_sel == 0)
  l_out$fal_neg_pcor <- sum(pcor_true != 0 & pcor_est_sel == 0)
  
  ## Sensitivity
  l_out$sens_beta <- l_out$true_pos_beta / (l_out$true_pos_beta + l_out$fal_neg_beta)
  l_out$sens_pcor <- l_out$true_pos_pcor / (l_out$true_pos_pcor + l_out$fal_neg_pcor)
  
  ## Specificity
  l_out$spec_beta <- l_out$true_neg_beta / (l_out$true_neg_beta + l_out$fal_pos_beta)
  l_out$spec_pcor <- l_out$true_neg_pcor / (l_out$true_neg_pcor + l_out$fal_pos_pcor)
  
  
  
  ## ...
  
  
  ## Coverage
  # Loop across different cred. ints
  df_ci <- data.frame(ci = cred_int,
                           sum_cover_beta = rep(NA, length(cred_int)),
                           sum_cover_pcor = rep(NA, length(cred_int)),
                           width_beta = rep(NA, length(cred_int)),
                           width_pcor = rep(NA, length(cred_int)) )
  for(i in 1:length(cred_int)){
    lb_beta <- cred_interval$beta_lb[[i]]
    ub_beta <- cred_interval$beta_ub[[i]]
    lb_pcor <- cred_interval$pcor_lb[[i]]
    ub_pcor <- cred_interval$pcor_ub[[i]]  
    
    m_cover_beta <- beta_true >= lb_beta & beta_true <= ub_beta 
    m_cover_pcor <- pcor_true >= lb_pcor & pcor_true <= ub_pcor 
    
    # Only consider upper diagonal of pcor
    df_ci[i, "sum_cover_beta"] <- sum(m_cover_beta)
    df_ci[i, "sum_cover_pcor"] <- sum(m_cover_pcor[upper.tri(m_cover_pcor)])
    
  }
  
  ## Average width

   for(i in 1:length(cred_int)){
    lb_beta <- cred_interval$beta_lb[[i]]
    ub_beta <- cred_interval$beta_ub[[i]]
    lb_pcor <- cred_interval$pcor_lb[[i]]
    ub_pcor <- cred_interval$pcor_ub[[i]]
    
    df_ci[i,"width_beta"] <- mean(ub_beta - lb_beta)
    df_ci[i,"width_pcor"] <- mean(ub_pcor[upper.tri(ub_pcor)] - lb_pcor[upper.tri(lb_pcor)])
    
   }
  
  l_out$ci <- df_ci
  
  

  #--- Output ---#

  return(l_out)
}
  
a <- l_res_bggm[[1]][[1]]$lb_beta
b <- l_res_bggm[[1]][[1]]$ub_beta
c <- l_graphs$graph1$beta
is_in_ci <- c >= a & c <= b
sum(is_in_ci)

eval_ex <- eval_bggm(l_res_bggm[[1]][[1]])

```




### Evaluate BGGM
```{r}
test_eval <- lapply(l_res_bggm[[1]], eval_bggm)

test_eval <- lapply(l_res_bggm, function(x){
  res <- lapply(x, eval_bggm)
  return(res)
})

```




```{r}


```












