---
title: "concatenating-var"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

# Data Generation

```{r}
library(tidyverse)
library(BGGM)
library(here)
library(ggplot2)
library(graphicalVAR)
library(qgraph)
library(parallel)
library(doParallel)
library(foreach)
library(doRNG)

```


```{r concatenate-ts}
# time series need to be standardized before concatenation
# we also need to assume stationarity 
# first just take the first two time series here


fried_net <- readRDS(here("data/graph_fried.Rds"))

graph_fried <- list()
graph_fried$beta <- fried_net$beta
graph_fried$kappa <- fried_net$kappa

# For now, delete 3 edges so that every dgp has 6 vars
graph_fried$beta <- graph_fried$beta[1:6, 1:6]
graph_fried$kappa <- graph_fried$kappa[1:6, 1:6]

# Storage
l_data <- list()
l_d <- list()
l_conc <- list()
l_out <- list()

# Data generation
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)
l_data <- foreach(i = seq(100), .packages = c("graphicalVAR")) %dopar% {
  # setup storage
  l_d <- list()
  l_conc <- list()
  l_out <- list()
  
  g <- graph_fried
  
  # Simulate data
  l_d$d1 <- graphicalVARsim(300, beta = g$beta, kappa = g$kappa, mean = 0)
  l_d$d2 <- graphicalVARsim(300, beta = g$beta, kappa = g$kappa, mean = 0)
  
  # Concatenate
  conc_12 <- rbind(l_d$d1, l_d$d2) 
  nr <- 600
  
  # Delete entries in the middle
  conc_12[(nr/2-2):(nr/2-2),] <- c(rep(NA, 6))
  l_conc <- conc_12
  
  
  l_out$l_d <- l_d
  l_out$l_conc <- l_conc
  
  return(l_out)
  
}
stopCluster(cl)

# Separate lists for fitting
# create a function to extract the two lists from each element
extract_lists <- function(x) {
  list(l_d = x$l_d, l_conc = x$l_conc)
}

# apply the function to each element of the original list using lapply
new_list <- lapply(l_data, extract_lists)

# extract the two lists from the new list using lapply and simplify = FALSE
l_d <- lapply(new_list, function(x) list(d1 = list(data = x$l_d$d1), d2 = list(data = x$l_d$d2)))
l_conc <- lapply(new_list, function(x) list(data = x$l_conc))






```





# Concatenating Time Series BGGM
This idea is based on Williams & Mulder (2020). Instead of comparing the posterior predictive estimations of two datasets directly, we could concatenate two time series under the null hypothesis that they originate from the same data-generating process. We could then compare the posterior predictive results from these concatenated time series to either a distribution from an individual time series or just a single test statistic. This is also comparable to Zhang, Templin & Mintz (2022) and chaining graphicalVARs for subgrouping. 


## Estimation
```{r}
# Estimate new model on concatenated dataset and on individual datasets
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000


# estimate models
l_conc_fit <- list()
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

# concatenated dataset
l_conc_fit <- fit_var_parallel_merged(dat = l_conc, 
                        n = 100, 
                        nds = 100,
                        rho_prior = rho_sd, 
                        beta_prior = beta_sd, 
                        seed = seed, 
                        iterations= n_iter)

# individual models
l_ind_fit <- fit_var_parallel_merged(data = l_d,
                        nds = 100,
                        n = 2,
                        rho_prior = 0.5, 
                        beta_prior = 1,
                        seed = 2022,
                        iterations = 5000,
                        posteriorsamples = FALSE,
                        multigroup = TRUE,
                        pruneresults = TRUE,
                        get_kappa = FALSE)

stopCluster(cl)

# Create reference distribution on concatenated time series
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

# Create reference distribution on concatenated time series
l_conc_postsim <- sim_from_post_parallel(l_conc_fit,
                                         n_datasets = 500,
                                         n = 100,
                                         tp = 600, 
                                         iterations = 5000,
                                         seed = 2022,
                                         means = 0)

# Then refit models to posterior simulated datasets
# TODO does not work yet

l_fit_post_res <- lapply(l_conc_postsim, function(x){
  fit_var_parallel_merged(data = x,
                        nds = 500,
                        n = 2,
                        rho_prior = 0.5, 
                        beta_prior = 1,
                        seed = 2022,
                        iterations = 5000,
                        posteriorsamples = FALSE,
                        multigroup = TRUE,
                        pruneresults = TRUE,
                        get_kappa = FALSE)})
stopCluster(cl)






# 
# post_res <- sim_from_post_concat(res_conc12, 
#                      n_datasets = 1000,
#                      n = 1000,
#                      tp = 600,
#                      iterations = 5000,
#                      seed = 2022)
# stopCluster(cl)



# create reference distribution
ref_dist <- lapply(fit_post_res, function(x){
  if(!is.na(x[[1]][1]) && !is.na(x[[2]][1])){
    norm(x[[1]]$beta_mu-x[[2]]$beta_mu, type = "F")
  }
})

conc_post_res <- data.frame(post = do.call(rbind, ref_dist),
                            emp = norm(res1$beta_mu - res2$beta_mu, type = "F"))

conc_post_res %>% 
  mutate(n_samp_smaller = sum(emp > post)) %>% 
  ggplot(aes(x = post))+
  geom_density()+
  geom_vline(aes(xintercept = emp))
    



### Then create posterior predictive datasets for each posterior sample and compute distances under the null 
# 
sim_from_post_concat <- function(fitobj, 
                                   n_datasets, 
                                   n,
                                   tp,
                                   iterations = 5000,
                                   seed = 2022,  
                                   means = 0,
                                   ngroups = 2){             # number of datasets create for each posterior slice
  require(doParallel)
  
  
  # Extract parameters from fitobject
  # delete first 50 samples
  l_params <- list()


  l_params$beta <- fitobj$fit$beta[,,51:iterations]
  l_params$kappa <- fitobj$fit$kappa[,,51:iterations]

  
  # reproducible parallelization
  # doRNG::registerDoRNG(seed)
  
  # Loop to create new datasets from posterior samples
  dat <- list()
  dat <- foreach(j = seq(n_datasets), .packages = "graphicalVAR") %dopar% {
      # get random posterior sample
      # Needs transposing of beta matrix!
      smp <- sample(iterations-50, size = 1)
      sim_dat <- list()
      
      
      for(g in seq(ngroups)){
      sim_dat[[g]] <- list()
      sim_dat[[g]]$data <- try(as.data.frame(graphicalVAR::graphicalVARsim(nTime = tp,
                                                                  beta = t(l_params$beta[,,smp]),
                                                                  kappa = l_params$kappa[,,smp],
                                                                  mean = means))) 


    }
    sim_dat
    
    
  } # end parallel
  

  dat
  
}


```







# Concatenating GraphicalVAR

Instead of using BGGM, we could also just use graphicalVAR to simulate from concatenated time series again and then refit. 
```{r}

# Need function for fitting in parallel
fit_gvar_parallel <- function(data,
                     nds,
                     n,     # n per group - TODO make this optional
                     simulated = FALSE,
                     multigroup = FALSE,
                     posteriorsamples = FALSE, 
                     pruneresults = TRUE,
                     ...){                     # arguments passed to graphicalVAR
  
  
  require(graphicalVAR)
  require(doParallel)
  # reproducible parallelization
  doRNG::registerDoRNG(seed)
  
  if(!multigroup & !posteriosamples ){
  fit <- foreach(i = seq(nds), .packages = "graphicalVAR") %dopar% {
      fit_ind <- tryCatch({graphicalVAR::graphicalVAR(data[[i]]$data,
                             ...)}, error = function(e) NULL)
      
      if(isTRUE(pruneresults)){
        beta <- fit_ind$beta 
        kappa <- fit_ind$kappa
        gamma <- fit_ind$gamma
        fit_ind <- list()
        fit_ind$beta <- beta
        fit_ind$kappa <- kappa
        fit_ind$gamma <- gamma
      }
  
      
      
      fit_ind
      
      }

  }

  
  if(isTRUE(multigroup)){
    fit <- foreach(i = seq(nds), .packages = "graphicalVAR") %dopar% {
      fit_ind <- list()
      for(d in seq(n)){
        if(is.list(data[[i]])){
          if(is.list(data[[i]][[d]])){
              fit_ind[[d]] <- tryCatch({graphicalVAR::graphicalVAR(data[[i]][[d]]$data,
                             ...)}, error = function(e) NULL)
        
        
              
              if(isTRUE(pruneresults) & length(fit_ind[[d]] > 0 )){
              beta <- fit_ind[[d]]$beta 
              kappa <- fit_ind[[d]]$kappa
              gamma <- fit_ind[[d]]$gamma
              fit_ind[[d]] <- list()
              fit_ind$beta <- beta
              fit_ind$kappa <- kappa
              fit_ind$gamma <- gamma
           } # end pruneresults
            
         } 
       }

        
     } # end loop across groups
      return(fit_ind)
      
      
      
    } # end foreach
    
    
  }  # end multigroup
  
  
  
  if(isTRUE(posteriorsamples)){
    fit <- foreach(i = seq(nds), .packages = "graphicalVAR") %dopar% {
      fit_ind <- list()
      for(d in seq(n)){
        if(is.list(data[[i]])){
          if(is.list(data[[i]][[d]])){
              fit_ind[[d]] <- tryCatch({graphicalVAR::graphicalVAR(data[[i]][[d]],
                             ...)}, error = function(e) NULL)
        
        
              
              if(isTRUE(pruneresults) & length(fit_ind[[d]] > 0 )){
              beta <- fit_ind[[d]]$beta 
              kappa <- fit_ind[[d]]$kappa
              gamma <- fit_ind[[d]]$gamma
              fit_ind[[d]] <- list()
              fit_ind$beta <- beta
              fit_ind$kappa <- kappa
              fit_ind$gamma <- gamma
           } # end pruneresults
            
         } 
       }

        
     } # end loop across groups
      return(fit_ind)
      
      
      
    } # end foreach
    
    
  } # end posteriorsamples
    

 return(fit)
  
  
  
}

# try it out
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

res <- fit_gvar_parallel(l_d, nds = 100, n = 2, multigroup = TRUE)
res_conc <- fit_gvar_parallel(l_conc, nds = 100)


stopCluster(cl)



# Need function for simulation from results in parallel 
# TODO: arguments arenot coherent across fns at the moment (n vs. nds vs. n_datasets)
sim_from_post_gvar <- function(fit, 
                               n, 
                               n_datasets = 1000, 
                               tp, 
                               means){
  
   post_sim <- foreach(i = seq(n), .packages = "graphicalVAR") %dopar% {   # loop over individuals
     dat <- list()
     for(j in seq(n_datasets)){        # loop over datasets to create
           dat[[j]] <- graphicalVAR::graphicalVARsim(nTime = tp,
                                  beta = fit[[i]]$kappa,
                                  kappa = fit[[i]]$kappa,
                                  mean = means)
       
       
     } # end seq(n_datasets)

    return(dat)
  } # end foreach
  return(post_sim)
  
}

# try it out
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

sim_conc <- sim_from_post_gvar(res_conc, n = 100, 
                               tp = 600, 
                               means = 0,
                               n_datasets = 100)

stopCluster(cl)




# Refit on all simulated datasets to create reference distribution
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

fit_conc_post <- fit_gvar_parallel(sim_conc, n = 100, nds = 100, posteriorsamples = TRUE)

stopCluster(cl)



```


## Evaluation










