---
title: "var-compare-empirical-example"
author: "Björn Siepe"
date: "`r Sys.Date()"
output: html_document
---

This document contains code to reproduce the empirical example section in the paper, as well as the prior illustration in the introduction. 
```{r}
library(BGGM)
library(qgraph)
library(tidyverse)
library(foreach)
library(doParallel)
library(parallel)
library(Hmisc)
library(imputeTS)
library(cowplot)
library(here)
source("aux_funs.R")
```



# Example prior distributions
Draw 5000 observations for temporal and contemporaneous priors. 
```{r}
set.seed(35037)
prior_samples <- 50000

## Temporal
# Simply sample from normal distribution
wide_beta <- rnorm(n = prior_samples, mean = 0, sd = 1)
narrow_beta <- rnorm(n = prior_samples, mean = 0, sd = 0.5)

## Contemporaneous
# Wide prior
wide_pcor <- BGGM::plot_prior(prior_sd = 0.5, iter = prior_samples)
wide_pcor <- wide_pcor$plot_env$prior_samp$pcors[1,2,]

# Narrow prior
narrow_pcor <- BGGM::plot_prior(prior_sd = 0.25, iter = prior_samples)
narrow_pcor <- narrow_pcor$plot_env$prior_samp$pcors[1,2,]

# Create dataframe
df_prior <- data.frame(
  value = c(wide_beta, narrow_beta, wide_pcor, narrow_pcor),
  mat = c(rep("Temporal",2*prior_samples), rep("Contemporaneous", 2*prior_samples)),
  prior = rep(c(rep("wide", prior_samples), rep("narrow", prior_samples)),2),
  label = c(rep("1", prior_samples), rep("0.5", prior_samples), rep("0.5", prior_samples), rep("0.25", prior_samples))
)

# Expressions
df_prior <- df_prior %>% 
  mutate(prior = factor(prior,
                        levels = c("wide", "narrow"),
                        labels = c(expression(wide~prior~(s[beta]~"= 1, "~ s[rho]~"= 0.5")),
                                   expression(narrow~prior~(s[beta]~"= 0.3, "~ s[rho]~"= 0.2")))),
         mat = as.factor(mat)) %>% 
  mutate(mat = forcats::fct_relevel(mat, "Temporal"))





# Create grid plot
prior_example <- df_prior %>% 
  ggplot(aes(x = value))+
  geom_density(fill = ggokabeito::palette_okabe_ito()[2],
               col = "black",
                 # bins = 50
               )+
  theme_compare()+
  # facet_grid(prior~mat, 
  #            scales = "free_x",
  #            labeller = label_parsed)+
  ggh4x::facet_grid2(
             prior~mat, 
             axes = "all",
             scales = "free_x",
             # remove_labels = "y",
             labeller = label_parsed)+
  labs(y = "",
       x = "")+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y = element_line(),
        axis.line.x = element_line(),
        strip.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 20),
        axis.text=element_text(size=rel(1.2)),
        panel.spacing.x = ggplot2::unit(2.5, "lines"))

prior_example
ggsave("prior_example_dens.svg", prior_example, path = here::here("figures/revision1") ,device = "svg", width = 10, height = 8)


```



# Empirical Example
We use data from Fisher et al. (2017), downloaded from https://osf.io/5ybxt/
Functions needed:
```{r}
lagpad <- function(x, k) {
     c(rep(NA, k), x)[1 : length(x)] 
 }
```


Then use code adapted from Fisher et al. https://osf.io/m63ks to perform cubic spline interpolation to resample to even time intervals for observations. 
```{r}
file_list <- list.files(path = here::here("data/empirical_example/fisher_2017"), pattern = ".RData", full.names = TRUE)

# Number of items
n_items <- 21
rel_items <-  c("energetic", "enthusiastic", "content", "irritable", "restless", "worried",  "guilty",  "afraid", "anhedonia", "angry", "hopeless", "down", 
"positive", "fatigue", "tension", "concentrate", "ruminate", "avoid_act", "reassure",  "procrast", "avoid_people")

l_data <- list()
for(i in 1:length(file_list)){
  l_data[[i]] <- list()
  load(file_list[[i]])
  
  # add lags
  data$lag=lagpad(data$start,1)

  # Calculate time differences
  data$tdif=as.numeric(difftime(strptime(data$start,"%m/%d/%Y %H:%M"),strptime(data$lag,"%m/%d/%Y %H:%M")))

  # Replace NA
  data$tdif[is.na(data$tdif)] <- 0
  
  # give names to columns with missing names
  # Get the index of NA column names
  na_cols <- which(is.na(colnames(data)))

  # Replace NA column names with new names
  colnames(data)[na_cols] <- paste0("new_name_", na_cols)
  
  # Calculate cumulative sum of numeric elapsed time
  data$cumsumT = cumsum(data$tdif)

  # Subset data
  trim=data[,c(3:18,21:24,28)]
  dedat=data.frame(matrix(ncol = dim(trim)[2], nrow = dim(trim[1])))
  colnames(dedat) <- colnames(trim)

  ### Detrend
  for(d in 1:n_items){
    dedat[,d] = resid(lm(scale(trim[,d])~data$cumsumT, na.action = na.exclude))
  }
  ### Cubic spline interpolation
  datcub <- data.frame(matrix(ncol=21,nrow=nrow(data)))
  for(d in 1:n_items){
    datcub[,d]=(spline(x = data$cumsumT, y=dedat[,d], nrow(data), method='fmm'))$y
  }
  colnames(datcub) <- colnames(dedat)
  
  # Only choose relevant data for us
  datcub <- datcub %>% 
    dplyr::select(c("content", "fatigue", "concentrate", "positive", "hopeless", "enthusiastic"))

  l_data[[i]] <- datcub
  
}
# remove everything but the data list
rm(list=setdiff(ls(), "l_data"))

```

Using new data by Aaron Fisher, where some beep issues have been fixed. 
```{r}
load("C:/Users/Bjoern/Drive/Academia/Projects/var-compare/data/empirical_example/Fisher_Raw_Data.RData")

files <- lapply(ls(pattern="dat"), function(x) get(x))
```





Description of missing data
```{r}
data <- bind_rows(l_data, .id = "id")
data %>% 
  group_by(id) %>% 
  count() %>% 
  ungroup() %>% 
  dplyr::summarize(mean_obs = mean(n))


```



# Fit new models
```{r}
rho_prior = 0.25
beta_prior = .5
iterations = 50000
seed = 2022

df_prior <- data.frame(
  rho_prior = c(0.1, 0.25, 0.5),
  beta_prior = c(0.25, 0.5, 1)
)


l_fits <- list()


cl = makeCluster(3)
registerDoParallel(cl)
l_fits <- foreach(i = 1:nrow(df_prior), .packages = "BGGM") %dopar% {
  r_p <- df_prior[i,"rho_prior"]
  b_p <- df_prior[i, "beta_prior"]
  
  fit <- lapply(l_data, function(x){
  tryCatch(BGGM::var_estimate(Y = x,      
                     rho_sd = r_p,
                     beta_sd = b_p,
                     iter = 50000,
                     seed = 2022), error = function(e) NA)

    
})

  return(fit)
}

stopCluster(cl)  
  
l_fits_c <- list()
for(i in 1:3){
  l_fits_c[[i]] <- lapply(l_fits[[i]], function(x){
  x$fit$Sigma <- NULL
  x$fit$fisher_z <- NULL
  x
})
  
}
# saveRDS(l_fits_c, here::here("output/empirical-example/l_fits.RDS"))
l_fits_c <- readRDS(here::here("output/empirical-example/l_fits.RDS"))
```



## Diagnostic plots 
Create diagnostic plots for the second prior combination here. 
```{r}
# Obtain parameter names
# nodes
p <- 6
# identity matrix
I_p <- diag(p)
# column names
cn_pcor <- colnames(l_fits_c[[2]][[1]]$pcor_mu)
cn_beta <- colnames(l_fits_c[[2]][[1]]$beta_mu)
rn_beta <- rownames(l_fits_c[[2]][[1]]$beta_mu)

names_pcor <- sapply(cn_pcor, function(x) paste(cn_pcor, x, sep = "--"))[upper.tri(I_p)]
names_beta <- sapply(rn_beta, function(x) paste(cn_beta, x, sep = "_"))
all_names <- c(names_pcor, names_beta)


# ACF plots 
pdf("figures/acf_plots_empirical.pdf")
for(i in 1:40){
  for(n in all_names){
  plt <- BGGM::convergence(l_fits_c[[2]][[i]], type = "acf", param = n)
  print(plt[[1]] + theme_compare() + labs(title = paste0("ID ", i)))
  }
}
dev.off()

# One example combination
acf_pcor <- BGGM::convergence(l_fits_c[[2]][[12]], type = "acf", param = "content--concentrate")
acf_beta <- BGGM::convergence(l_fits_c[[2]][[12]], type = "acf", param = "content_concentrate.l1")

plot_pcor <- acf_pcor[[1]]+
  theme_compare()+
  labs(title = "Contemporaneous")

plot_beta <- acf_beta[[1]]+
  theme_compare()+
  labs(title = "Temporal")

plot_acf_example <- cowplot::plot_grid(plot_pcor, plot_beta)
ggsave("plot_acf_example.svg", plot_acf_example, device = "svg", path = here::here("figures/"), width = 12, height = 6)


# Trace plots
pdf("figures/trace_plots_empirical.pdf")
for(i in 1:40){
  for(n in all_names){
  plt <- BGGM::convergence(l_fits_c[[2]][[i]], type = "trace", param = n)
  print(plt[[1]] + theme_compare() + labs(title = paste0("ID ", i)))
  }
}
dev.off()
BGGM::convergence(l_fits_c[[2]][[12]], type = "trace", param = "concentrate--hopeless")

# One example combination
trace_pcor <- BGGM::convergence(l_fits_c[[2]][[12]], type = "trace", param = "content--concentrate")
trace_beta <- BGGM::convergence(l_fits_c[[2]][[12]], type = "trace", param = "content_concentrate.l1")

plot_pcor <- trace_pcor[[1]]+
  theme_compare()+
  labs(title = "Contemporaneous")

plot_beta <- trace_beta[[1]]+
  theme_compare()+
  labs(title = "Temporal")

plot_trace_example <- cowplot::plot_grid(plot_pcor, plot_beta)
ggsave("plot_trace_example.svg", plot_trace_example, device = "svg", path = here::here("figures/"), width = 12, height = 6)


# Get ESS for all samples
l_ess <- lapply(l_fits_c[[2]], var_ess)

# Obtain statistics about ESS 
ess_beta <- list()
ess_pcor <- list()
for(i in 1:40){
  ess_beta[[i]] <- l_ess[[i]]$ess_beta
  arr_beta <- do.call(rbind, lapply(ess_beta, as.numeric))
  
  ess_pcor[[i]] <- l_ess[[i]]$ess_pcor
  arr_pcor <- do.call(rbind, lapply(ess_pcor, as.numeric))
}
# Calculate means
mean(colMeans(arr_beta))
mean(colMeans(arr_pcor)[colMeans(arr_pcor)!=0])


# calculate mean ess per individual
ind_ess_beta <- sapply(l_ess, function(x) mean(x$ess_beta))
min(ind_ess_beta)
max(ind_ess_beta)

ind_ess_pcor <- sapply(l_ess, function(x) mean(x$ess_pcor[x$ess_pcor!=0]))
min(ind_ess_pcor)
max(ind_ess_pcor)
```


# Test
Test across all participants and across different priors. I ran into some memory issues here, so I splitted based on priors.
We use compare_var instead of within_compare from the simulation study here because I improved the function after having 
computed all simulation results. The improvements were only for clarity/performance, results are the same. 
```{r}
l_fits <- l_fits_c
fit_grid <- expand.grid(fit_a = 1:length(l_fits[[1]]), 
                        fit_b = 1:length(l_fits[[1]]), 
                        priors = seq(nrow(df_prior), 1), 
                        comp = c("l1", "frob", "maxdiff"))
l_comps <- list()

cl = makeCluster(14)
registerDoParallel(cl)
clusterExport(cl, c("compare_var", "post_distance_within"))
l_fits_1 <- l_fits[[1]]
fit_grid_1 <- fit_grid %>% 
  filter(priors == 1)
l_comps_1 <- foreach(i = 1:nrow(fit_grid_1)) %dopar% {
  
  # Extract information
  a <- fit_grid_1$fit_a[i]
  b <- fit_grid_1$fit_b[i]
  p_ind <- fit_grid_1$priors[i]
  compa <-  as.character(fit_grid_1$comp[i])


  
  if(is.list(l_fits_1[[a]]) & is.list(l_fits_1[[b]])){

  comp_res  <- compare_var(l_fits_1[[a]],l_fits_1[[b]], comp = compa)

  return(comp_res)
  }
  else
    return(NA)
  
}



l_fits_2 <- l_fits_c[[2]]
fit_grid_2 <- fit_grid %>% 
  filter(priors == 2)
l_comps_2 <- foreach(i = 1:nrow(fit_grid_2)) %dopar% {
  
  # Extract information
  a <- fit_grid_2$fit_a[i]
  b <- fit_grid_2$fit_b[i]
  p_ind <- fit_grid_2$priors[i]
  compa <-  as.character(fit_grid_2$comp[i])

  
  if(is.list(l_fits_2[[a]]) & is.list(l_fits_2[[b]])){
  comp_res  <- compare_var(l_fits_2[[a]],l_fits_2[[b]], comp = compa)

  return(comp_res)
  }
  else
    return(NA)
  
  
    
  
  
}

rm(l_fits_2)



l_fits_3 <- l_fits_c[[3]]
fit_grid_3 <- fit_grid %>% 
  filter(priors == 3)
l_comps_3 <- foreach(i = 1:nrow(fit_grid_3)) %dopar% {
  
  # Extract information
  a <- fit_grid_3$fit_a[i]
  b <- fit_grid_3$fit_b[i]
  p_ind <- fit_grid_3$priors[i]
  compa <-  as.character(fit_grid_3$comp[i])

  
  if(is.list(l_fits_3[[a]]) & is.list(l_fits_3[[b]])){

  comp_res  <- compare_var(l_fits_3[[a]],l_fits_3[[b]], comp = compa)

  return(comp_res)
  }
  else
    return(NA)
  
}
stopCluster(cl)
rm(l_fits_3)

df_comps2_1 <- do.call(rbind, l_comps_1)
df_comps2_2 <- do.call(rbind, l_comps_2)
df_comps2_3 <- do.call(rbind, l_comps_3)

# Add prior information
df_comps2_1c <- df_comps2_1 %>% 
  cbind(fit_grid_1)
df_comps2_2c <- df_comps2_2 %>% 
  cbind(fit_grid_2)
df_comps2_3c <- df_comps2_3 %>% 
  cbind(fit_grid_3)



df_compsc <- as.data.frame(rbind(df_comps2_1c, df_comps2_2c, df_comps2_3c))

# delete unnecessary columns
df_comps <- df_compsc %>% 
  dplyr::select(-c(larger_beta, larger_pcor)) %>% 
  as.data.frame()

# saveRDS(df_comps, file = here::here("data/empirical_example/df_comps_cubicspline.RDS"))

df_comps <- readRDS(here::here("data/empirical_example/df_comps_cubicspline.RDS"))
```


## Prior Sensitivity Plot
```{r}
# Calculate amount of possible combinations per condition
# 1560
# we count all comparisons twice, which is useless, but also does not change results
df_comps %>% 
  filter(fit_a != fit_b) %>% 
  group_by(priors, comp) %>% 
  count()


prior_names <- c(
  "1" = "Rho: 0.1, Beta: 0.25",
  "2" = "Rho: 0.25, Beta: 0.5",
  "3" = "Rho: 0.5, Beta: 1"
)


# Summarize information
df_comps_summary <- df_comps %>% 
  dplyr::filter(fit_a != fit_b) %>% 
  dplyr::mutate(across(c(contains("beta"), contains("pcor")),
                ~as.numeric(.))) %>% 
  dplyr::group_by(priors, comp) %>% 
  dplyr::summarize(sum_sig_beta = sum(ifelse(sig_beta >0, 1, 0)),
            sum_sig_pcor = sum(ifelse(sig_pcor >0, 1, 0)),
            mean_emp_beta = mean(emp_beta, na.rm =  TRUE)) %>% 
  dplyr::mutate(prop_sig_beta = sum_sig_beta / 1560,
         prop_sig_pcor = sum_sig_pcor / 1560) %>% 
  pivot_longer(cols = c("sum_sig_beta", "sum_sig_pcor"), names_to = "mat_sum", values_to = "sum") %>% 
  pivot_longer(cols = c("prop_sig_beta", "prop_sig_pcor"), names_to = "mat_prop", values_to = "prop")


emp_ex_prior_sensitivity <- df_comps_summary %>% 
  ggplot(aes(x = comp, y = prop, group = mat_prop, fill = mat_prop))+
  geom_bar(position = "dodge", stat = "identity")+
  # geom_point()+
  # geom_segment(aes(x = prop, xend = prop, y = 0, yend = comp))+
  # coord_flip()+
  facet_wrap(priors~., labeller = as_labeller(prior_names))+
  theme_compare()+
  ggokabeito::scale_fill_okabe_ito(labels = c("Temporal", "Contemporaneous"))+
  scale_y_continuous(limits = c(0,1),labels = function(x) paste0(x*100, "%"))+
  labs(x = "Norm",
       y = "Proportion Significant",
       # title = "Prior Sensitivity Empirical Example",
       fill = "Matrix")
emp_ex_prior_sensitivity

ggsave("emp_ex_prior_sensitivity_cubicspline.svg", emp_ex_prior_sensitivity, device = "svg", path = here::here("figures/"), width = 7, height = 5)

```


## Plot networks

```{r}
plot_net <- function(fit_obj){
  par(mfrow=c(1,2))
  qgraph::qgraph(fit_obj$beta_mu, title = "Temporal", theme = "colorblind", layout = "circle")
  qgraph::qgraph(fit_obj$pcor_mu, title = "Contemporaneous", theme = "colorblind", layout = "circle")
}


```


## Example: No evidence for differences
8 and 29
```{r}
# Look for examples with no evidence for diffs
df_comps %>% 
  filter(priors == 2) %>% 
  filter(fit_a != fit_b) %>% 
  filter(comp == "frob") %>% 
  mutate(across(c(contains("sig"), contains("emp")),
                ~as.numeric(.))) %>% 
  filter(sig_beta == 0 & sig_pcor == 0) %>% View()

# find number of observations
n_obs <- do.call(rbind, lapply(l_data, function(x) nrow(x)))

# Choose pair with similar n 
# 18 and 12
fit_12 <- l_fits_c[[2]][[12]]
fit_18 <- l_fits_c[[2]][[18]]

# Compare
res_emp_comp <- compare_var(fit_12, fit_18, return_all = TRUE)

# calculate median edge difference
mean(abs(fit_12$beta_mu-fit_18$beta_mu))
mean(abs(fit_12$pcor_mu[upper.tri(fit_12$pcor_mu, diag = FALSE)]-fit_18$pcor_mu[upper.tri(fit_18$pcor_mu, diag = FALSE)]))

# calcute number of sign differences
sum(sign(fit_12$beta_mu) != sign(fit_18$beta_mu))
sum(sign(fit_12$pcor_mu[upper.tri(fit_12$pcor_mu, diag = FALSE)]) != sign(fit_18$pcor_mu[upper.tri(fit_18$pcor_mu, diag = FALSE)]))

# Plot automatically
plot.compare_var(res_emp_comp, name_a = "ID 12", name_b = "ID 18")


```

Create network plots below each other, then plot the comparison.
Do this manually to have more control beyond the functions.
Note that the study ID used for the plot is unequal to iteration ID used here. 
```{r}
# First, all the networks
svg(filename = "figures/empirical_temp_networks.svg")
par(mfrow=c(1,2))
p12_temp <- qgraph::qgraph(fit_12$beta_mu, theme = "colorblind", layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[1])

p18_temp <- qgraph::qgraph(fit_18$beta_mu, theme = "colorblind", layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[2])

dev.off()

svg(filename = "figures/empirical_cont_networks.svg")
par(mfrow=c(1,2))

p12_cont <- qgraph::qgraph(fit_12$pcor_mu, theme = "colorblind", layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[1])
p18_cont <- qgraph::qgraph(fit_18$pcor_mu, theme = "colorblind", layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[2])
dev.off()



## Find edge for scaling
max_sc<- max(c(max(abs(fit_12$beta_mu)), max(abs(fit_12$pcor_mu)), max(abs(fit_18$beta_mu)), max(abs(fit_18$pcor_mu))))


# Plot individually
svg(filename = "figures/empirical_network_12t.svg")

p12_temp <- qgraph::qgraph(fit_12$beta_mu, 
                           theme = "colorblind", 
                           layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[1], 
                           maximum = max_sc, 
                           negDashed = TRUE)
dev.off()

svg(filename = "figures/empirical_network_18t.svg")
p18_temp <- qgraph::qgraph(fit_18$beta_mu, 
                           theme = "colorblind", 
                           layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[2], 
                           maximum = max_sc, 
                           negDashed = TRUE)
dev.off()

svg(filename = "figures/empirical_network_12c.svg")
p12_cont <- qgraph::qgraph(fit_12$pcor_mu, 
                           theme = "colorblind", 
                           layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[1], 
                           maximum = max_sc, 
                           negDashed = TRUE)
dev.off()

svg(filename = "figures/empirical_network_18c.svg")

p18_cont <- qgraph::qgraph(fit_18$pcor_mu, 
                           theme = "colorblind", 
                           layout = "circle",
                           color = ggokabeito::palette_okabe_ito()[2], 
                           maximum = max_sc, 
                           negDashed = TRUE)
dev.off()



# Then, comparison for temporal and contemporaneous
plt_beta <- 
  res_emp_comp$res_beta %>%
    mutate(mod = case_match(mod,
                            "mod_a" ~ "ID 19",
                            "mod_b" ~ "ID 40")) %>% 
    ggplot(aes(x = null, fill = mod, linetype = mod))+
    geom_density(alpha = .7)+
    ggokabeito::scale_fill_okabe_ito()+
    geom_vline(aes(xintercept = res_emp_comp$emp_beta), 
               col = "black", lty = 1, linewidth = .75)+
    scale_y_continuous(expand = c(0,0.05))+
    theme_compare()+
    labs(y = "",
         x = "Norm Value",
         fill = "",
         linetype = "",
         title = "Test")+
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "right",
          legend.key.height= unit(0.5, 'cm'),
          legend.key.width= unit(1, 'cm'),
          plot.title = element_text(face = "plain", family = "news", size = 9, hjust = 0))
plt_beta

plt_pcor <- 
  res_emp_comp$res_pcor %>%
    mutate(mod = case_match(mod,
                            "mod_a" ~ "ID 19",
                            "mod_b" ~ "ID 40")) %>% 
    ggplot(aes(x = null, fill = mod, linetype = mod))+
    geom_density(alpha = .7)+
    ggokabeito::scale_fill_okabe_ito()+
    geom_vline(aes(xintercept = res_emp_comp$emp_pcor), 
               col = "black", lty = 1, linewidth = .75)+
    scale_y_continuous(expand = c(0,0.05))+
    labs(y = "",
         x = "Norm Value",
         title = "")+
    theme_compare()+
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "right", 
          plot.title = element_text(face = "plain", family = "news", size = 9, hjust = 0))

leg <- cowplot::get_legend(plt_beta)
  
# Plot
plt_tmp <- cowplot::plot_grid(plt_beta + theme(legend.position = "none"),
                              plt_pcor + theme(legend.position = "none"))

# Add legend
# plt <- plot_grid(plt_tmp, leg, rel_widths = c(3, .4))
plt <- plt_tmp 
plt

plt_pcor

# Figure had to be created manually because qgraph cannot be used by cowplot...
svg_12t <- magick::image_read_svg(here::here("figures/empirical_network_12t.svg"))
svg_12c <- magick::image_read_svg(here::here("figures/empirical_network_12c.svg"))
svg_18t <- magick::image_read_svg(here::here("figures/empirical_network_18t.svg"))
svg_18c <- magick::image_read_svg(here::here("figures/empirical_network_18c.svg"))


plt_12t <- ggdraw() + 
  draw_image(svg_12t, scale = 1) +
  draw_label("ID 12", x = 0.1, y = 0.85, fontfamily = "news", size = 9)
plt_12t
plt_12c <- ggdraw() + 
  draw_image(svg_12c, scale = 1)
plt_18t <- ggdraw() + 
  draw_image(svg_18t, scale = 1) + 
  draw_label("ID 18", x = 0.1, y = 0.85, fontfamily = "news", size = 9)
plt_18c <- ggdraw() + draw_image(svg_18c, scale = 1)

row_12 <- plot_grid(plt_12t, plt_12c, 
                    labels = c("Temporal", "Contemporaneous"),
                    label_size = 14,
                    label_fontfamily = "news",
                    label_x = c(-0.1, -0.2))
row_18 <- plot_grid(plt_18t, plt_18c)


full_plot <- plot_grid(
  row_12,
  row_18,
  plt,
  nrow = 3,
  rel_heights = c(1,1,0.7)
)

ggsave("full_plot_empirical_example_dashed.svg", full_plot, device = "svg", height = 8.5, width = 6, 
       path = here::here("figures/"))

```


## Posterior matrix
Idea: Plot posterior distributions, color based on if the parameter is positive or not. 
```{r}
fit <- l_fits_c[[1]][[1]]

plot_example_posterior <- tsnet::posterior_plot(fit, mat = "beta")+
  theme(legend.title = element_text(size = rel(1.3)))

plot_example_posterior

ggsave("plot_example_posterior_beta.svg", plot_example_posterior, 
       device = "svg", path = here::here("figures/"), width = 20, height = 12, 
       units = "cm")

ggsave("plot_example_posterior_beta.png", plot_example_posterior, 
       device = "png", path = here::here("figures/"), width = 10, height = 8, 
       units = "cm")



```



# Matched Comparisons
Based on a recent preprint by Ebrahimi et al. (2023), we can also only compare individuals with a similar severity of depression, which may be a more meaningful comparison than just comparing everyone. 

We use the HAM-D and HAM-A scores from https://osf.io/uuz4y to match participants.
Only use one of the priors: 
```{r}
# Load fitted models
l_fits <- l_fits_c[[2]]

# Load depression and anxiety scores
df_hamd <- readxl::read_xlsx(here("data/empirical_example/fisher_2017/fisher_2017_hamd.xlsx"))

df_hamd <- df_hamd %>% 
  janitor::clean_names()


```


## Matching individuals
We only form groups of two by nearest-neighbour search.
```{r}
library(RANN)

# nearest neigbhour search (ignoring ID col)
nn <- RANN::nn2(df_hamd[,-1], df_hamd[,-1], k = 2)

# delete first column, which just finds the datapoints themselves
nn_ids <- nn$nn.idx[,-1]

# except for id 9 and 30
nn_ids[9] <- 29
nn_ids[30] <- 2


```


## Testing
All relevant combinations:
```{r}
fit_grid_match <- data.frame(fit_a = 1:40, 
                        fit_b = nn_ids, 
                        comp =  "frob")

priors <- df_prior[2,]

# compare all
cl = makeCluster(14)
registerDoParallel(cl)
clusterExport(cl, c("compare_var", "post_distance_within"))
l_comp_match <- foreach(i = 1:nrow(fit_grid_match)) %dopar% {
  
  # Extract information
  a <- fit_grid_match$fit_a[i]
  b <- fit_grid_match$fit_b[i]
  compa <-  as.character(fit_grid_match$comp[i])


  
  if(is.list(l_fits[[a]]) & is.list(l_fits[[b]])){

  comp_res  <- compare_var(l_fits[[a]],l_fits[[b]], comp = compa)

  return(comp_res)
  }
  else
    return(NA)
  
}
stopCluster(cl)


```


## Summarize results

```{r}
df_comps_match <- do.call(rbind, l_comp_match)
df_comps_match %>% 
  as.data.frame() %>% 
  dplyr::select(sig_beta, sig_pcor) %>% 
  unnest() %>% 
  mutate(sig_beta = ifelse(sig_beta != 0, 1, 0),
         sig_pcor = ifelse(sig_pcor != 0, 1, 0)) %>% 
  summary()

``` 



