---
title: "graveyard"
author: "Björn Siepe"
date: "2022-11-16"
output: html_document
---

# Fit VAR models
```{r}
# model_a <- mgm::mvar(data = dat,
#                      type = rep("g", 6),
#                      level = rep(1,6),
#                      lambdaSel = "EBIC",
#                      lambdaGam = 0,
#                      lags = 1,
#                      consec = 1:nrow(dat),
#                      threshold = "none", 
#                      scale = TRUE)
# 
# 
# model_b <- mgm::mvar(data = dat,
#                      type = rep("g", 6),
#                      level = rep(1,6),
#                      lambdaSel = "EBIC",
#                      lambdaGam = 0,
#                      lags = 1,
#                      consec = 1:nrow(dat),
#                      threshold = "none", 
#                      scale = TRUE)
# 
# ntime_a <- length(model_a$call$data_lagged$included)
# pars_a <- model_a$wadj[,,1]
# int_a <- unlist(model_a$intercepts)
# 
# # the intercepts are so small that the data afterwards becomes weird
# # so I manually set the intercepts
# int_a <- c(-0.3, 0.1, 0.05, -0.25, 0.4, 0.01)

```



Now we simulate 100 models from the parameters of $A$. 
```{r}
# # setup parallelization
# ncores = parallel::detectCores() - 4
# cl = makeCluster(ncores)
# registerDoParallel(cl)
# 
# # somehow, the following gives me insanely weird data, basically everything is almost zero
# l_dat <- foreach(i = 1:100, .packages = "mlVAR") %dopar% {
#   mod <- simulateVAR(pars = pars_a,
#                      means = 0,
#                      Nt = ntime_a,
#                      residuals = 1)     # need to check if I should provide residual covariance matrix here
#   mod
#   
# }
# 
# 
# # fit model A to the data 100 times
# l_res_a <- foreach(i = 1:100, .packages = "mgm") %dopar% {
#   res <- predict(object = model_a, 
#                  data = l_dat[[i]])
#   errors <- res$errors
# }
# 
# # slightly change model B and fit to the data again
# for(i in 1:nrow(model_b$wadj[,,1])){
#   for(j in 1:ncol(model_b$wadj[,,1])){
#     if(model_b$wadj[,,1][i,j]>0.0001 | model_b$wadj[,,1][i,j] < -0.0001){
#       model_b$wadj[,,1][i,j] <- model_b$wadj[,,1][i,j] + rnorm (n = 1,mean = 0.05, sd = 0.01)
#     }
#   }
# }
# 
# l_res_b <- foreach(i = 1:100, .packages = "mgm") %dopar% {
#   res <- predict(object = model_b, 
#                  data = l_dat[[i]])
#   errors <- res$errors
# }
# 
# 
# stopCluster(cl)

```

This does not give a nice distribution with uncertainty.
It also gives me negative R² values, which is really weird, probably
due to the insanely small variance?
Maybe I should resample from the VAR model using the uncertainty
in $\beta$ and then compare distributions. 




## Compare error distribution to slightly different model
Add small random noise to the coefficients of the "true" model and refit to data.
This is not trivial, because the "predict" function uses posterior samples
to evaluate the prediction and not just the posterior mean. Maybe I should rewrite the function so that just the mean is used to obtain predictions.
```{r}
# slightly change model B and fit to the data again
# only change nonzero coefs
# bay_res_b <- bay_res
# for(i in 1:nrow(bay_res_b$beta_mu)){
#   for(j in 1:ncol(bay_res_b$beta_mu)){
#     if(bay_res_b$beta_mu[i,j]!=0){
#       bay_res_b$beta_mu[i,j] <- bay_res_b$beta_mu[i,j]+rnorm(1, mean = 0, sd = 0.25)
#     }
#   }
# }
# 
# ncores = parallel::detectCores() - 4
# cl = makeCluster(ncores)
# registerDoParallel(cl)
# l_refit <- foreach(i = 1:100) %dopar% {
#   source("aux_funs.R")
#   ref <- predict(object = bay_res_b,
#                  data = l_dat[[i]])
#   
# } 
# 
# 
# stopCluster(cl)
```








## Older Stuff


Another idea: for each posterior sample, generate two new datasets and obtain Frobenius norm between the two regression matrices for each sample as Null distribution. 
```{r}
# takes as input one posterior sample
# generates two new datasets, re-estimates the model and then 
# computes frobenius norm between resulting estimates
# this does not work well because there is not enough error 
frob_res <- c(rep(NA, 100))
for(i in 51:151){
  frob_res[i] <- f_post_frob(l_res[[1]]$fit$beta[,,i])
}

df_frob_res <- as.data.frame(frob_res)
df_frob_res <- na.omit(df_frob_res)
df_frob_emp <- as.data.frame(frob_emp)
df_frob_emp <- na.omit(df_frob_emp)



df_frob_res %>% 
  filter(!is.na(frob_res)) %>% 
  ggplot(aes(x = frob_res))+
  geom_density()+
  geom_vline(aes(xintercept = quantile(frob_res, 0.95), col = "red"))+
  geom_point(data = df_frob_emp, aes(x = frob_emp, y = 0), col = "blue")+
  theme_minimal()


```




For later, obtain the likelihoods of each model directly and then compare these across samples. 
```{r}

```












# Older Stuff

## Refitting approach
Refit all models to all 100 datasets. Use the internal function by Williams, modified by me.

Do I even need the intercept when all time series are standardized? He seems to ignore them. I also still need to understand what the 'predict' function does here and if it is even useful for me. The predict function uses the posterior samples to predict fitted values, so it even contains the foundation for the new simulated datasets? Not sure if this makes sense. Here we are however interested in the comparison of the graph that will actually be plotted, so just use the posterior mean of the beta coefficients for prediction.


This is not functioning at the moment because there is a new list layer to l_dat_bggm. 
```{r}
ncores = parallel::detectCores() - 8
cl = makeCluster(ncores)
registerDoParallel(cl)

# change i to n_ind or so
l_refit <- foreach(i = seq(2), .export = c("predict_pmu.var_estimate"))  %dopar% { # each model
  l_m_ref <- list()  # store for each model
  for(j in 1:n_postds){   # each simulated dataset
    l_m_ref[[j]] <- try(predict_pmu.var_estimate(object = l_res[[i]],
                             data = l_dat_bggm[[j]]))
  }
  return(l_m_ref)
} 



stopCluster(cl)
```

We use RMSE to evaluate the fit, but could also use Bayesian $R^2$ or similar stuff (maybe even the likelihood). As we get credible intervals for the predictions, we could also do something with structure recovery, so see which edges were included and which weren't if we opt for some kind of sparsity. 

```{r compute-rmse}
l_rmse <- list()
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
l_rmse <- foreach(i = seq(n_ind)) %dopar% {  # for every model 
  df_rmse <- data.frame(iter = 1:n_ds,
                    rmse = rep(NA, n_ds),
                    model = rep(i, n_ds))
  for(j in 1:n_postds){      # for every dataset
    df_rmse[j,"rmse"] <- try(f_eval_refit(data = l_dat_bggm[[j]],
               refit = l_refit[[i]][[j]]))
  }
  return(df_rmse)
}

stopCluster(cl)
df_errors <- do.call(rbind, l_rmse)
# write_rds(df_errors, "df_errors.Rds")
```


Plot the error distribution:
```{r plot-error-dist}
df_errors %>% 
  mutate(rmse = as.numeric(rmse)) %>% 
  mutate(rmse = round(rmse, 3)) %>% 
  filter(model < 10) %>% 
  ggplot(aes(x = rmse, group = model , fill = as.factor(model), col = as.factor(model)))+
  ggdist::stat_halfeye(alpha = 0.7)+
  theme_minimal()+
  ggokabeito::scale_fill_okabe_ito()+
  ggokabeito::scale_color_okabe_ito()

```


Two ways of numerical comparison: First, treat as empirical distribution and use Kolmogorow-Smirnow. P-Values can be computed exactly or with Monte Carlo Sampling, I need to check which one makes the most sense. Apparently, the KS test (and similar tests) assume independence between the curves under consideration. 
```{r comp-kstest}
# Loop over test statistics
# Baseline is model 1
err1 <- df_errors$rmse[df_errors$model == 1]
df_ks_res <- data.frame(model = rep(NA, n_mod),
                        statistic = rep(NA, n_mod),
                        pval = rep(NA, n_mod))
options(scipen=999)

# Filter model that did not converge, have to do this more principled later on
df_errors <- df_errors %>% 
  mutate(rmse = as.numeric(rmse)) %>% 
  filter(!is.na(rmse))

for(m in 2:n_mod){
  if(m != 75){
  err_alt <- df_errors$rmse[df_errors$model == m]
  tmp <- stats::ks.test(x = err1,
                 y = err_alt,
                 alternative = "greater")
  df_ks_res[m,"model"] <- m
  df_ks_res[m, "statistic"] <- tmp$statistic[[1]]
  df_ks_res[m, "pval"] <- round(tmp$p.value, 5)
  }

}

# Still too many false positives?
# maybe I should actually test one-sided, because some of the models
# actually fit better than the reference model
sum(df_ks_res$pval < 0.001, na.rm = TRUE)



```

Second, estimate density, treat as empirical distribution and calculate Jenson-Shannon-Divergence (which is symmetrical, KL-Divergence is not).
The exact method for estimating the density should not matter too much, as the distribution of errors should roughly follow a normal distribution. For now, just use the density approach in the `stats` package with a Gaussian kernel. 1-JSD is a similarity metric. 
```{r}

# compute for whole dataset
jsd_res <- f_comp_jsd(df = df_errors, n = 100)

jsd_res %>% 
  ggplot(aes(x = jsd))+
  geom_density()+
  theme_minimal()


```


Another idea: compute something like absolute difference between network results, as van Borkulo et al. did it. 
```{r}

```





# Concatenating Time Series
Another idea is based on Williams & Mulder (2020). Instead of comparing the posterior predictive estimations of two datasets directly, we could concatenate two time series under the null hypothesis that they originate from the same data-generating process. We could then compare the posterior predictive results from these concatenated time series to either a distribution from an individual time series or just a single test statistic. This is also comparable to Zhang, Templin & Mintz (2022). 

```{r concatenate-ts}
# time series need to be standardized before concatenation
# we also need to assume stationarity 
# first just take the first two time series here
conc_12 <- rbind(l_dat[[1]]$Y, l_dat[[3]]$Y)

# delete first entry of second time series to create gap
# conc_12[nrow(conc_12)/2+1,] <- c(NA, NA, NA, NA, NA, NA)

# delete multiple entries in the middle of the time series to create gap
conc_12[197:201,] <- c(rep(NA, 6))

# Estimate new model on concatenated dataset
# Fit the model
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000

# estimate model on concatenated dataset
res_conc12 <- BGGM::var_estimate(conc_12,
                                   rho_sd = rho_sd,
                                   beta_sd = beta_sd,
                                   iter = n_iter,
                                   progress = FALSE,
                                   seed = seed)

# results are very different compared to just one model
res_conc12$beta_mu
l_res[[1]]$beta_mu
l_res[[2]]$beta_mu
t(graph$beta)


```





Just a quick check on how well parameters are recovered: 
```{r}
test <- list()
for(i in 1:length(l_res)){
  test[[i]] <- l_res[[i]]$beta_mu
}
a_test <- array(unlist(test), c(6,6,100))

# means across refit samples
rowMeans(a_test, dims = 2)
# comparison with ground truth
t(graph$beta)
```




















