---
title: "many_networks_gif"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

Just creating a .gif with many networks that "look" different as a visual starting point for discussing heterogeneity. 

Simulate from the same DGP with low number of observations, then fit and plot resulting networks.

```{r}
library(graphicalVAR)
library(qgraph)
library(animation)
library(foreach)
library(parallel)
library(doParallel)
library(tidyverse)
source("aux_funs.R")
set.seed(35037)

l_graphs <- readRDS(here::here("data/l_graphs.RDS"))
dgp <- l_graphs[[5]]

# create two larger edges
dgp$beta[1,2] <- .4
dgp$beta[5,3] <- -.4

# make some negative
dgp$beta[1,3] <- dgp$beta[1,3] * -1
dgp$beta[5,4] <- dgp$beta[2,3] * -1
dgp$beta[5,2] <- dgp$beta[2,3] * -1


# Simulate
ncores = 10
cl = makeCluster(ncores)
clusterExport(cl = cl, "fit_graphicalvar_parallel")
registerDoParallel(cl)
data_list <- sim_raw_parallel(dgp = dgp,
                                    n = 50,      # 50 individuals
                                    tp = 70,
                                    seed = 35037,
                                    means = 0,
                                    standardize = TRUE)


# Fit in parallel

# res_list  <- fit_graphicalvar_parallel(data_list,
#                                        seed = 35037,
#                                                   n = 50,
#                                                   gamma = 0,
#                                                   nLambda = 50, 
#                                                   pruneresults = FALSE)


stopCluster(cl)

# Save data for sharing
sim_data <- lapply(data_list, function(x){
  x$data
})

saveRDS(sim_data, here::here("data/gvar_sim_data.RDS"))
```


Visualize into gif

```{r}

animation::saveGIF({
  for(i in 1:50){
      par(mfrow = c(1,2))
    qgraph(res_list[[i]]$PDC, 
       title = "Temporal", 
       title.cex = 1.9,
       theme = "colorblind", 
       layout = "circle", 
       mar = c(4,4,4,4))
    qgraph(res_list[[i]]$PCC, 
       title.cex = 1.9,
       title = paste("Contemporaneous     ID", i), 
       theme = "colorblind", 
       layout = "circle", 
       mar = c(4,4,4,4))}
  }, movie.name = "many_network_gif.gif", interval = .5,
  ani.width = 800, ani.height = 600

)


```

Individual images

```{r}
for(i in 1:20){
  png(paste0("figures/gif/network_", i, ".png"), width = 960, height = 960, res = 150) 
   par(mfrow = c(1,2))
    qgraph(res_list[[i]]$PDC, 
       title = "Temporal", 
       title.cex = 1.2,
       theme = "colorblind", 
       layout = "circle", 
       mar = c(4,4,4,4))
    qgraph(res_list[[i]]$PCC, 
       title.cex = 1.2,
       title = paste("Contemporaneous          ID", i), 
       theme = "colorblind", 
       layout = "circle", 
       mar = c(4,4,4,4))
  dev.off()
}

```


# Instead use GIMME indSEM
This is for illustration what can go wrong if we use GIMME on a dataset that is from a single DGP. 

```{r}
gimme_list <- lapply(data_list, function(x){
  x$data
})

gimme_res <- gimme::indSEM(data = sim_data)

mean_paths <- Reduce("+", gimme_res$path_est_mats) / length(gimme_res$path_est_mats)
mad_paths <- 
  Reduce("+", lapply(gimme_res$path_est_mats, function(x){
    abs(x - mean_paths)
  })) / length(gimme_res$path_est_mats)

which.max(mad_paths)
```
V1 -> V4
```{r}
gimme_res$path_se_est %>% 
  filter(lhs == "V1" & rhs == "V4")
```

Look at a group-level effect
```{r}
meta_res <- gimme_res$path_se_est %>% 
  filter(level == "group") %>% 
  filter(lhs == "V1" & rhs == "V1lag")

# Create a forest plot in ggplot
library(ggplot2)

for_plot <- meta_res %>% 
  ggplot(aes(x = beta, y = file)) +
  geom_vline(xintercept = 0.24, 
             linetype = "dashed", 
             color = "red",
             size = .75)+
  geom_point() +
  geom_errorbarh(aes(xmin = beta - 1.96 * se, xmax = beta + 1.96 * se)) +
  geom_vline(xintercept = 0)+
  theme_compare()+
  labs(x = "Example Autoregressive Effect", y = "ID",
       title = "Data of 50 individuals with identical true effects")+
  theme(axis.text.y = element_blank())+
  scale_x_continuous(breaks = seq(-.5, 1.5, .5),
                     limits = c(-.6, 2))

ggsave(here::here("figures/forest_plot.pdf"), for_plot, width = 7, height = 7)

```

Put it in a meta-analysis
```{r}
library(metaBMA)
library(meta)
test_meta <- metaBMA::meta_bma(y = meta_res$beta, SE = meta_res$se,
                        labels = meta_res$file, data = meta_res)

meta_meta <- meta::metamean(n = rep(70, 50), 
               mean = meta_res$beta, 
               sd = meta_res$se)



```



# Without AR path

```{r}
gimme_no_ar <- gimme::indSEM(data = gimme_list, 
                             ar = FALSE)

gimme_no_ar$path_se_est %>% 
  group_by(lhs, rhs) %>% 
  count() %>% 
  arrange(desc(n))


# look at the effect that was estimated most often 
res_no_ar <- gimme_no_ar$path_se_est %>% 
  filter(lhs == "V5" & rhs == "V3lag")

res_no_ar <- gimme_no_ar$path_se_est %>% 
  filter(lhs == "V3" & rhs == "V1lag")

# Compute effect with highest SD
gimme_no_ar$path_se_est %>% 
  group_by(lhs, rhs) %>% 
  summarise(mad = mad(beta),
            n = n()) %>% 
  arrange(desc(n))

res_no_ar <- gimme_no_ar$path_se_est %>% 
  filter(lhs == "V2" & rhs == "V3")


# Create a forest plot in ggplot
library(ggplot2)
res_no_ar %>% 
  ggplot(aes(x = beta, y = file)) +
  geom_point() +
  geom_errorbarh(aes(xmin = beta - 1.96 * se, xmax = beta + 1.96 * se)) +
  geom_vline(xintercept = 0)+
  theme_minimal()+
  labs(x = "Effect", y = "ID")+
  geom_vline(xintercept = 0.095, linetype = "dashed", color = "red")




```


