---
title: "var-resample"
author: "Björn Siepe"
date: "2022-11-10"
output: html_document
---

# Background

Goal is to compare if two VAR models $A$ and $B$ are really different from another. We use resampling to do this. \## Idea: 1. Fit $A$ and $B$ to their respective data. 2. Using parameters of $A$, generate $n$ new time series. 3. Refit $A$ and $B$ on each of the $n$ time series. 4. Obtain measure of fit, such as $MSE$. 5. Compare error distributions, either by cutoff or something like a Divergence. (6. Maybe repeat the other way around, so sampling from $B$?)

I use a developmental version of the BGGM package that returns the covariance matrix of residuals for each posterior sample. I need this to sample new data.
TODO: Change BGGM library everywhere.
```{r preparations, include = FALSE}
library(tidyverse)
library(graphicalVAR)
library(doParallel)
library(mgm)
library(mlVAR)
library(BGGM)
# library("BGGM", lib.loc = "C:/Users/Bjoern/R-dev")
library(reshape2)      # Data manipulation
library(mvtnorm)       # Sim from posterior
library(stats)         # KS-Test
library(philentropy)   # divergence measures
library(todor)         # keep on track with stuff to do
source("aux_funs.R")
library(ggokabeito)
library(Matrix)
library(here)
here::i_am("var-compare.Rproj")
```



Dataset overview:
- l_raw: Contains `n_mod` datasets sampled from specific DGP.
- l_res: Contains `n_ind`fitted models, one for each l_raw. Represents different people under same DGP.  
- l_params: Contains posterior beta and kappa matrices for each fitted model in l_res.
- 

New data-generating processes by Hoekstra:
She used PDC and PCC instead of beta and kappa. Maybe I won't use her dgps after all. 
For now, pretend that she used beta and kappa, so we likely use a bit sparser graphs than she did.
```{r dgp-hoekstra}
```

```{r dgp-epskamp2018}
# take Kappa and Beta from Epskamp et al.(2018), having reproduced the analysis in their supplement 2
# 7 Node graph ,especially beta is VERY sparse
# Maybe this is TOO sparse and I should use the graphs from Mansueto et al. 
beta_eps <- as.matrix(read.table(header = FALSE, colClasses = "numeric", text = "
0        0            0                  0   0.000000       0.0000000             0.00000000
0        0            0                  0   0.000000       0.0000000             0.00000000
0        0            0                  0   0.000000       0.0000000             0.24128652
0        0            0                  0   0.000000       0.0000000             0.00000000
0        0            0                  0   0.243744       0.0000000             0.00000000
0        0            0                  0   0.000000       0.2293295             0.07956604
0        0            0                  0   0.000000       0.1099387             0.00000000"))
# Correct small rounding differences (6th digit) in Kappa
# correct by using lower diagonal, not rounded values
kappa_eps <- as.matrix(read.table(header = FALSE, colClasses = "numeric", text = "
 1.167983844  0.134688900 0.009096612   -0.128603055  0.133407195  0.000000000        0.225946298
 0.134688940  1.130350300 0.000000000    0.000000000 -0.337813000  0.000000000       -0.064444800
 0.009096612  0.000000000 1.468400008    0.000000000  0.000000000  0.000000000        0.000000000
-0.128603055  0.000000000 0.000000000    1.106057060  0.000000000  0.000000000        0.071637710
 0.133407195 -0.337813000 0.000000000    0.000000000  1.286898100  0.000000000        0.000000000
 0.000000000  0.000000000 0.000000000    0.000000000  0.000000000  1.256290950       -0.086044850
 0.225946298 -0.064444800 0.000000000    0.071637710  0.000000000 -0.086044850        1.159429540"))
graph_eps <- list()
graph_eps$beta <- beta_eps
kappa_eps<- as.matrix(Matrix::forceSymmetric(kappa_eps, uplo = "L"))
graph_eps$kappa <- kappa_eps
pcc_eps <- -cov2cor(kappa_eps)
graph_eps$PCC <- pcc_eps
diag(graph_eps$PCC) <- rep(0,7)
dimnames(graph_eps$beta) <- NULL
dimnames(graph_eps$kappa) <- NULL
```


```{r dgp-chain graph}
# Create a chain graph, which is good to estimate with VAR models


```


```{r generate-graph}
# Ground truth model is still generated with graphicalVAR 
# could also use empirical data with varying sparsity
set.seed(2022)    # does NOT help here with model creation! need to write own function
og_graph <- randomGVARmodel(Nvar = 6, probKappaEdge = 0.5, probBetaEdge = 0.3)
beta <- as.matrix(read.table(header = FALSE, colClasses = "numeric", text = "
 0.2266407 0.0000000  0.0000000 -0.2668593  0.0000000 0.0000000
-0.7380388 0.2266407  0.0000000  0.0000000 -0.9288327 0.0000000
 0.0000000 0.0000000  0.2266407  0.9571318  0.2409225 0.5543485
 0.0000000 0.0000000  0.0000000  0.2266407 -0.7438448 0.0000000
 0.5214148 0.0000000  0.0000000  0.0000000  0.2266407 0.0000000
 0.0000000 0.0000000 -0.8903007  0.0000000  0.0000000 0.2266407"))
kappa <- as.matrix(read.table(header = FALSE, colClasses = "numeric", text = "
 1.0000000  0.0000000  0.0000000 0.0000000  0.4018933 0.3717013
 0.0000000  1.0000000  0.2266407 0.5527593 -0.2654634 0.2593779
 0.0000000  0.2266407  1.0000000 0.0000000 -0.3318945 0.3175423
 0.0000000  0.5527593  0.0000000 1.0000000  0.0000000 0.0000000
 0.4018933 -0.2654634 -0.3318945 0.0000000  1.0000000 0.0000000
 0.3717013  0.2593779  0.3175423 0.0000000  0.0000000 1.0000000"))

# compute partial correlations from kappa
# in the case of only 1s on the diagonal of kappa, this just changes the sign
pcc <- -cov2cor(kappa)
graph <- list()
graph$beta <- beta
graph$kappa <- kappa
graph$PCC <- pcc
diag(graph$PCC) <- rep(0,6)
dimnames(graph$beta) <- NULL
dimnames(graph$kappa) <- NULL

graph2 <- graph
graph2$beta <- graph2$beta + runif(36, -0.05, 0.05)
graph2$kappa <- graph2$kappa + runif(36, -0.05, 0.05)
diag(graph2$kappa) <- c(1,1,1,1,1,1)
graph2$kappa <- Matrix::forceSymmetric(graph2$kappa)
l_graph <- list(graph = graph,
                graph2 = graph2)
```

Now we can change all graphs according to the simulation conditions.
```{r change-graphs}
# Store graphs as list
l_graphs <- list(graph1 = graph, 
                 graph2 = graph, 
                 graph3 = graph)

# Apply change function to every graph
l_changed_graphs <- lapply(l_graphs, 
                           function(x) {change_graphs(
                                            truegraph = x, 
                                            changemax = c(1.2, 1.5, 1.7),
                                            noise = c(0.1,0.2,0.3))})


```



Then, generate rawdata from data-generating processes. We create more posterior datasets than we fit in the end, because some of them do not converge. 
TODO: This will need changes when we add multiple simulation conditions. 
```{r generate-rawdata}
# Storage
l_raw <- list()
# Simulation conditions
n_ind <- 100   # number of individuals (so models to create)
n_tp <- 100     # number of timepoints per time series
n_postds <- 130     # number of posterior datasets


# Think about if I actually need to standardize here
# because everything will be standardized by var_estimate anyway
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
l_raw$graph <- lapply(l_changed_graphs$graph1, 
                      function(x) {sim_raw_parallel(
                                dgp = x, n = n_postds, 
                                tp = n_tp, means = 0,
                                standardize = TRUE)})
# l_raw$graph2 <- lapply(l_changed_graphs$graph2, 
#                       function(x) {sim_raw_parallel(
#                                 dgp = x, n = n_postds, 
#                                 tp = n_tp, means = 0,
#                                 standardize = TRUE)})
# l_raw$graph3 <- lapply(l_changed_graphs$graph3, 
#                       function(x) {sim_raw_parallel(
#                                 dgp = x, n = n_postds, 
#                                 tp = n_tp, means = 0,
#                                 standardize = TRUE)})

stopCluster(cl)
```

Rewrite this to handle multiple data-generating processes at once: 
```{r generate-rawdata-parallel}
# Storage
l_raw <- list()

# Simulation conditions
n_ind <- 15 # number of individuals(so models to create) TODO change back to 100
n_tp <- c(50,100,200,300) # number of timepoints
n_postds <- 130  # number of posterior datasets

# Think about if I actually need to standardize here
# because everything will be standardized by var_estimate anyway
# TODO loop over timepoints to use
before_simraw <- Sys.time()
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)
l_raw$graph1 <- list()
for(t in seq_along(n_tp)){
  l_raw$graph1[[t]] <- list()
  l_raw$graph1[[t]] <- lapply(l_changed_graphs$graph1, 
                                  function(x) {sim_raw_parallel(
                                    dgp = x, 
                                    n = n_ind, 
                                    tp = n_tp[t], 
                                    means = 0,
                                    standardize = TRUE)})
  
  l_raw$graph2[[t]] <- list()
  l_raw$graph2[[t]] <- lapply(l_changed_graphs$graph1, 
                                  function(x) {sim_raw_parallel(
                                    dgp = x, 
                                    n = n_ind, 
                                    tp = n_tp[t], 
                                    means = 0,
                                    standardize = TRUE)})
  l_raw$graph3[[t]] <- list()
  l_raw$graph3[[t]] <- lapply(l_changed_graphs$graph3, 
                                  function(x) {sim_raw_parallel(
                                    dgp = x, 
                                    n = n_ind, 
                                    tp = n_tp[t], 
                                    means = 0,
                                    standardize = TRUE)})
  
  
}



after_simraw <- Sys.time()-before_simraw  # less than 4 minutes



```



# Bayesian approach
Fit a VAR model to each raw dataset. 
```{r estimate-models}
# Bayesian model parameters
rho_sd <- 0.5      # Prior for covariance matrix
beta_sd <- 1       # Prior for regression matrix
seed <- 2022
n_iter <- 5000


l_res <- list()
l_res2 <- list()
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)
l_res <- fit_var_parallel(data = l_raw$graph, n = n_ind,
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
                 iterations = n_iter)
l_res2 <- fit_var_parallel(data = l_raw$graph2, n = n_ind,
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
                 iterations = n_iter)
stopCluster(cl)
# write_rds(l_res, "l_res.Rds")
# l_res <- read_rds("l_res.Rds")
# write_rds(l_res2, "l_res2.Rds")
# l_res2 <- read_rds("l_res2.Rds")
```
Rewrite to handle all simulation conditions.
```{r}
# Bayesian model parameters
rho_sd <- 0.5      # Prior for covariance matrix
beta_sd <- 1       # Prior for regression matrix
seed <- 2022
n_iter <- 5000

l_res <- list()
l_res$graph3 <- l_res$graph2 <- l_res$graph1 <-  list()

before_fitraw <- Sys.time()
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)
# Loop over timepoints condition
for(t in seq_along(n_tp)){
  l_res$graph1[[t]] <- lapply(l_raw$graph1[[t]], function(x){fit_var_parallel(
    data = x, n = n_ind, rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
    iterations = n_iter, pruneresults = TRUE
  )})
    l_res$graph2[[t]] <- lapply(l_raw$graph2[[t]], function(x){fit_var_parallel(
    data = x, n = n_ind, rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
    iterations = n_iter, pruneresults = TRUE
  )})
    l_res$graph3[[t]] <- lapply(l_raw$graph3[[t]], function(x){fit_var_parallel(
    data = x, n = n_ind, rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
    iterations = n_iter, pruneresults = TRUE
  )}) 
  
}


stopCluster(cl)
after_fitraw <- Sys.time()-before_fitraw

```




Comparison of results with grahpicalVAR is done in another script ("bggm-var-investigation.Rmd"). Here, we look at how well our model recovered the correct parameters. 
```{r recovery}
rec_res <- compare_dgp(graph, est_bggm = l_res, comp_gvar = FALSE, est_gvar = NULL)
```



## Directly use posterior samples

Use random samples from the posterior to simulate new datasets. 
```{r simulate-from-posterior}
## data generation first dgp
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)
l_data <- list()
l_data <- sim_from_post_parallel(fitobj = l_res, n = n_ind, n_datasets = n_postds, tp = n_tp,
                       iterations = n_iter, means = 0, convert_bggm = FALSE)
stopCluster(cl)

## second dgp
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)
l_data2 <- list()
l_data2 <- sim_from_post_parallel(fitobj = l_res2, n = n_ind, n_datasets = n_postds, tp = n_tp,
                       iterations = n_iter, means = 0, convert_bggm = FALSE)
stopCluster(cl)
# write_rds(l_data, "l_data.Rds")
# write_rds(l_data2, "l_data2.Rds")
# l_data <- read_rds("l_data.Rds")
# l_data2 <- read_rds("l_data2.Rds")

```
Rewrite for simulation conditions:
```{r}
# Create storage
l_data <- list()
l_data$graph3 <- l_data$graph2 <- l_data$graph1 <- list()


# Setup parallel
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

# Loop over timepoint conditions
for(t in seq_along(n_tp)){
  l_data$graph1[[t]] <- lapply(l_res$graph1[[t]], function(x){sim_from_post_parallel(
    fitobj = x, n = n_ind, n_datasets = n_postds, tp = n_tp,
    iterations = n_iter, means = 0, convert_bggm = FALSE)})
  
  l_data$graph2[[t]] <- lapply(l_res$graph2[[t]], function(x){sim_from_post_parallel(
    fitobj = x, n = n_ind, n_datasets = n_postds, tp = n_tp,
    iterations = n_iter, means = 0, convert_bggm = FALSE)})
  
  l_data$graph3[[t]] <- lapply(l_res$graph3[[t]], function(x){sim_from_post_parallel(
    fitobj = x, n = n_ind, n_datasets = n_postds, tp = n_tp,
    iterations = n_iter, means = 0, convert_bggm = FALSE)})
}

stopCluster(cl)


```







## Norm Approach
Compute different norms between models on resampled datasets compared to reference model and then compare to actual difference between two models. 

First, fit VAR model to posterior sample data. 
```{r fit-posterior}
# Fit the model to posterior data samples
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000


ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
l_postresfull <- list()
before_par2 <- Sys.time()
l_postres_all <- fit_var_parallel_post(data = l_data, n = 100, nds = n_postds,
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
                 iterations = n_iter, posteriorsamples = TRUE, pruneresults = TRUE) 
after_par2 <- before_par2 - Sys.time()
stopCluster(cl)
# Cut away failed attempts, always get 100 fitted results
l_postres <- lapply(l_postres_all, function(x) x[!sapply(x, is.null)])

# write_rds(l_postres, "l_postres.Rds")
# l_postres <- read_rds("l_postres.Rds")

# # Another DGP
# Use new function
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
l_postresfull <- list()
before_par2 <- Sys.time()
l_postres2_full <- fit_var_parallel_post(data = l_data2, n = 100, nds = n_postds,
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed,
                 iterations = n_iter, posteriorsamples = TRUE, pruneresults = TRUE) 
after_par2 <- before_par - Sys.time()
stopCluster(cl)

# Cut away failed attempts, always get 100 fitted results
l_postres2 <- lapply(l_postres2_full, function(x) x[!sapply(x, is.null)])

# write_rds(l_postres2, "l_postres2.Rds")
# l_postres2 <- read_rds("l_postres2.Rds")



```


Then, start the evaluation for identical DGP. 
TODO: Add comparison with resampled estimates within a group, so compare post1 with post 3, postX with postY, like a bootstrap
```{r same-dgp}
# Compare all possible combinations
comp_combinations <- expand_grid_unique(mod_a = seq(1, n_ind, 1),
                                 mod_b = seq(1, n_ind, 1))
# Number of comparison types
n_c_types <- 3

# Number of comparison combinations
n_c_comb <- nrow(comp_combinations)

comp_conditions <- data.frame(
                        postpost = rep(FALSE, n_c_comb*n_c_types),
                        mod_a = rep(comp_combinations[,1], n_c_types),
                        mod_b = rep(comp_combinations[,2], n_c_types),
                        fitpost_a = rep("l_postres", n_c_comb*n_c_types),
                        fitpost_b = rep("l_postres", n_c_comb*n_c_types), 
                        fitemp_a = rep("l_res", n_c_comb*n_c_types),
                        fitemp_b = rep("l_res", n_c_comb*n_c_types),
                        n_datasets = rep(100, n_c_comb*n_c_types),
                        comparison = c(rep("frob", n_c_comb), 
                                       rep("maxdiff", n_c_comb),
                                       rep("l1", n_c_comb)))
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
starttime <- Sys.time()
cross_compare_res <- list()
cross_compare_res <- 
  lapply(c(1:nrow(comp_conditions)), function(i){
    args <- comp_conditions[i,]
    cross_compare(
      mod_a = args$mod_a, 
      mod_b = args$mod_b,
      fitpost_a = eval(as.name(paste(args$fitpost_a))),
      fitpost_b = eval(as.name(paste(args$fitpost_b))), 
      fitemp_a = eval(as.name(paste(args$fitemp_a))), 
      fitemp_b = eval(as.name(paste(args$fitemp_b))), 
      n_datasets = args$n_datasets, 
      comparison = args$comparison
    )
    }
  )
stoptime <- Sys.time()-starttime    # ~16 seconds for 4950 comparisons!
stopCluster(cl)

# Build plot for results
eval_res <- lapply(cross_compare_res, cross_compare_eval)
df_eval_res <- as.data.frame(do.call(rbind, eval_res))
# write_rds(df_eval_res, "df_eval_res.Rds")
# df_eval_res <- read_rds("df_eval_res.Rds")

df_eval_res %>% 
  mutate(beta_a = as.numeric(beta_a),
         beta_b = as.numeric(beta_b),
         pcor_a = as.numeric(pcor_a),
         pcor_b = as.numeric(pcor_b),
         comp = as.factor(as.character(comp))) %>% 
  group_by(comp) %>% 
  # number of tries per condition
  add_count(comp) %>% 
  summarize(sig_beta = sum(beta_a < 5 & beta_b < 5)/n,
            sig_pcor = sum(pcor_a < 5 & pcor_b < 5)/n) %>% 
  ungroup() %>% 
  distinct(comp, sig_beta, sig_pcor)
plot_test_samedgp_75 <- df_eval_res %>% 
  pivot_longer(cols = c(beta_a, beta_b, pcor_a, pcor_b), names_to = "res") %>% 
  mutate(value = as.numeric(value),
         comp = as.character(comp)) %>% 
  ggplot(aes(x = value, color = comp, fill = comp))+
  geom_bar()+
  theme_minimal()+
  scale_fill_okabe_ito()+
  scale_color_okabe_ito()+
  labs(title = "Count of posterior differences larger than empirical",
       subtitle = "Simulating from same DGP (Epskamp, 2018)",
       caption = "200 Timepoints, 100 Individuals")+
  facet_wrap(~comp)+
  theme(legend.position = "none")
# ggsave("figures/plot_test_samedgp_eps200.svg", plot_test_samedgp_eps500,  device = "svg",
       # height = 12, width = 16, units = "cm")
```


Then look at different DGP. 
```{r different-dgp}
# Compare all possible combinations
comp_combinations2 <- expand_grid_unique(mod_a = seq(1, n_ind, 1),
                                 mod_b = seq(1, n_ind, 1))
comp_conditions2 <- data.frame(
                        postpost = rep(FALSE, nrow(comp_combinations2)*3),
                        mod_a = rep(comp_combinations2[,1], 3),
                        mod_b = rep(comp_combinations2[,2], 3),
                        fitpost_a = rep("l_postres", nrow(comp_combinations2)*3),
                        fitpost_b = rep("l_postres2", nrow(comp_combinations2)*3), 
                        fitemp_a = rep("l_res", nrow(comp_combinations2)*3),
                        fitemp_b = rep("l_res2", nrow(comp_combinations2)*3),
                        n_datasets = rep(100, nrow(comp_combinations2)*3),
                        comparison = c(rep("frob", nrow(comp_combinations2)), 
                                       rep("maxdiff", nrow(comp_combinations2)),
                                       rep("l1", nrow(comp_combinations2))))
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
starttime <- Sys.time()
cross_compare_res2 <- list()
cross_compare_res2 <- 
  lapply(c(1:nrow(comp_conditions2)), function(i){
    args <- comp_conditions2[i,]
    cross_compare(
      mod_a = args$mod_a, 
      mod_b = args$mod_b,
      fitpost_a = eval(as.name(paste(args$fitpost_a))),
      fitpost_b = eval(as.name(paste(args$fitpost_b))), 
      fitemp_a = eval(as.name(paste(args$fitemp_a))), 
      fitemp_b = eval(as.name(paste(args$fitemp_b))), 
      n_datasets = args$n_datasets, 
      comparison = args$comparison
    )
    }
  )
stoptime <- Sys.time()-starttime    # ~16 seconds for 4950 comparisons!
stopCluster(cl)
# Build plot separated by PCOR and BETA and by comparison type
eval_res2 <- lapply(cross_compare_res2, cross_compare_eval)
df_eval_res2 <- as.data.frame(do.call(rbind, eval_res2))
plot_test_comp2 <- df_eval_res2 %>% 
  pivot_longer(cols = -comp, 
               names_to = c("matrix", ".value"),
               names_sep = "_") %>% 
  pivot_longer(cols = c(a,b), values_to = "value", names_to = "ref_model") %>% 
  mutate(value = as.numeric(value),
         comp = as.character(comp)) %>% 
  ggplot(aes(x = value, color = comp, fill = comp))+
  geom_histogram(bins = 100, alpha =0.8)+
  theme_minimal()+
  scale_fill_okabe_ito()+
  scale_color_okabe_ito()+
  labs(title = "Count of posterior differences larger than empirical",
       subtitle = "Simulating from different DGP (random uniform noise [-0.05, 0.05])",
       caption = "75 Timepoints, 100 Individuals")+
  facet_grid(comp~matrix)
ggsave("figures/plot_test_runifnoise75.svg", plot_test_comp2,  device = "svg",
       height = 12, width = 16, units = "cm")
```





## Compare with full posterior differences
Instead of only taking the empirical difference between fits, we generate a distribution of posterior differences. 

```{r posterior-differences}
post_diff <- cross_compare_post(comparison = "l1")
post_diff %>% 
  bind_rows(., .id = "matrix") %>% 
  pivot_longer(cols = c("null", "emp"), names_to = "dist") %>% 
  ggplot(aes(x = value, group = dist, color = dist, fill = dist))+
  geom_density()+
  theme_minimal()
```



