---
title: "var-resample"
author: "Björn Siepe"
date: "2022-11-10"
output: html_document
---

# Background

Goal is to compare if two VAR models $A$ and $B$ are really different from another. We use resampling to do this. \## Idea: 1. Fit $A$ and $B$ to their respective data. 2. Using parameters of $A$, generate $n$ new time series. 3. Refit $A$ and $B$ on each of the $n$ time series. 4. Obtain measure of fit, such as $MSE$. 5. Compare error distributions, either by cutoff or something like a Divergence. (6. Maybe repeat the other way around, so sampling from $B$?)

I use a developmental version of the BGGM package that returns the covariance matrix of residuals for each posterior sample. I need this to sample new data.
```{r preparations, include = FALSE}

library(tidyverse)
library(graphicalVAR)
library(doParallel)
library(mgm)
library(mlVAR)
# library(BGGM)
library("BGGM", lib.loc = "C:/Users/Bjoern/R-dev")
library(reshape2)      # Data manipulation
library(mvtnorm)       # Sim from posterior
library(stats)         # KS-Test
library(philentropy)   # divergence measures
library(todor)         # keep on track with stuff to do
source("aux_funs.R")
```



Dataset overview:
- l_raw: Contains `n_mod` datasets sampled from specific DGP.
- l_res: Contains `n_ind`fitted models, one for each l_raw. Represents different people under same DGP.  
- l_params: Contains posterior beta and kappa matrices for each fitted model in l_res.
- 

Get ground truth model from empirical data: 
```{r}



```




```{r generate-graph}
# Ground truth model is still generated with graphicalVAR 
# could also use empirical data with varying sparsity
set.seed(2022)    # does NOT help here with model creation! need to write own function
og_graph <- randomGVARmodel(Nvar = 6, probKappaEdge = 0.5, probBetaEdge = 0.3)

beta <- as.matrix(read.table(header = FALSE, colClasses = "numeric", text = "
 0.2266407 0.0000000  0.0000000 -0.2668593  0.0000000 0.0000000
-0.7380388 0.2266407  0.0000000  0.0000000 -0.9288327 0.0000000
 0.0000000 0.0000000  0.2266407  0.9571318  0.2409225 0.5543485
 0.0000000 0.0000000  0.0000000  0.2266407 -0.7438448 0.0000000
 0.5214148 0.0000000  0.0000000  0.0000000  0.2266407 0.0000000
 0.0000000 0.0000000 -0.8903007  0.0000000  0.0000000 0.2266407"))

kappa <- as.matrix(read.table(header = FALSE, colClasses = "numeric", text = "
 1.0000000  0.0000000  0.0000000 0.0000000  0.4018933 0.3717013
 0.0000000  1.0000000  0.2266407 0.5527593 -0.2654634 0.2593779
 0.0000000  0.2266407  1.0000000 0.0000000 -0.3318945 0.3175423
 0.0000000  0.5527593  0.0000000 1.0000000  0.0000000 0.0000000
 0.4018933 -0.2654634 -0.3318945 0.0000000  1.0000000 0.0000000
 0.3717013  0.2593779  0.3175423 0.0000000  0.0000000 1.0000000"))
graph <- list()
graph$beta <- beta
graph$kappa <- kappa
dimnames(graph$beta) <- NULL
dimnames(graph$kappa) <- NULL



# add slight change of one model parameter to the list
graph2 <- graph
graph2$beta[which.max(graph2$beta)] <- graph2$beta[which.max(graph2$beta)]*1.5
  
l_graph <- list(graph = graph, 
                graph2 = graph2)









# Idea for the future: don't simulate (50, 100, 300, 500) observations,
# but just simulate 500 and then subsample from it. Then datasets are matched.
# # maybe DON'T DO THIS! If I standardize these data again when estimating a VAR
# # model, the data changes. 



```


```{r generate-rawdata}
# Storage
l_raw <- list()

# Simulation conditions
n_ind <- 100   # number of individuals (so models to create)
n_tp <- 100     # number of timepoints per time series
n_postds <- 100     # number of posterior datasets to create 


l_raw <- list()

# Think about if I actually need to standardize here
# because everything will be standardized by var_estimate anway

ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)


l_raw$graph <- sim_raw_parallel(dgp = graph, n = n_ind, 
                                tp = n_tp, means = 0,
                                standardize = TRUE)
l_raw$graph2 <- sim_raw_parallel(dgp = graph2, n = n_ind, 
                                 tp = n_tp, means = 0,
                                 standardize = TRUE)

stopCluster(cl)
```


# Bayesian approach

Idea: Use the posterior distribution to obtain a variance-covariance matrix of the parameters, then sample 100 different datasets from these parameters?

```{r estimate-models}
# Bayesian model parameters
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000

# l_res <- list()
# for(i in seq(n_ind)){
#   l_res[[i]] <- try(BGGM::var_estimate(l_raw_sub[[i]],
#                                    rho_sd = rho_sd,
#                                    beta_sd = beta_sd,
#                                    iter = n_iter,
#                                    progress = FALSE,
#                                    seed = seed))
#   # Invert covariance matrix of residuals to obtain precision matrix
#   l_res[[i]]$fit$kappa <- array(apply(l_res[[i]]$fit$Sigma, 3, solve), 
#                                 dim = dim(l_res[[i]]$fit$Sigma))
# 
# }
# 
# l_res2 <- list()
# for(i in seq(n_ind)){
#   l_res2[[i]] <- try(BGGM::var_estimate(l_raw2_sub[[i]],
#                                    rho_sd = rho_sd,
#                                    beta_sd = beta_sd,
#                                    iter = n_iter,
#                                    progress = FALSE,
#                                    seed = seed))
#   # Invert covariance matrix of residuals to obtain precision matrix
#   l_res2[[i]]$fit$kappa <- array(apply(l_res2[[i]]$fit$Sigma, 3, solve), 
#                                 dim = dim(l_res2[[i]]$fit$Sigma))
# }



l_res <- list()
l_res2 <- list()
ncores = parallel::detectCores() - 2
cl = makeCluster(ncores)
registerDoParallel(cl)

l_res <- fit_var_parallel(data = l_raw$graph, n = 100, 
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed, 
                 iterations = n_iter)


l_res2 <- fit_var_parallel(data = l_raw$graph2, n = 100, 
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed, 
                 iterations = n_iter)

stopCluster(cl)



```

Compare results with graphicalVAR estimation.
```{r}
# l_res_gvar <- list()
# for(i in seq(n_ind)){
#   l_res_gvar[[i]] <- try(graphicalVAR(l_raw[[i]],
#                                    gamma = 0, 
#                                    lambda_beta = 0,
#                                    lambda_kappa = 0,
#                                    verbose = FALSE))
# 
# }


```







## Directly use posterior samples

Take the first 100 samples from the posterior of the first model (after deleting warmup samples).
```{r simulate-from-posterior}

# setup foreach for data generation
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)

l_data <- list()
l_data <- sim_from_post_parallel(fitobj = l_res, n = n_ind, n_datasets = n_postds, tp = n_tp,
                       iterations = n_iter, means = 0, convert_bggm = FALSE)


stopCluster(cl)

# TODO: maybe use own function to simulateVAR model, this gives me weird results
# Could also use sth. inspired by here: https://github.com/jmbh/ARVAR/blob/master/aux_functions.R

# DO I HAVE TO TRANSPOSE THE BETA MATRIX HERE?!?!?!
# DIFFERENT FORMAT IN BGGM and graphicalVAR
# put 1 on diagonal of matrix

# IMPORTANT! KAPPA IS NOT EQUAL TO PCOR MATRIX. KAPPA = PRECISION MATRIX


```

## Frobenius Norm Approach
Another idea: Compute Frobenius norm between models on resampled datasets compared to reference model and then compare to actual difference between two models. 
```{r}

# Fit the model to posterior data samples
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000

# Same DGP
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
l_postres <- list()

before <- Sys.time()

l_postres <- lapply(l_data, function(x) fit_var_parallel(data = x, n = 100, 
                 rho_prior = rho_sd, beta_prior = beta_sd, seed = seed, 
                 iterations = n_iter, posteriorsamples = TRUE, pruneresults = TRUE) )
after <- before - Sys.time()
stopCluster(cl)


# Compare all possible combinations
comp_combinations <- expand_grid_unique(mod_a = seq(1, n_ind, 1),
                                 mod_b = seq(1, n_ind, 1))

comp_conditions <- data.frame(mod_a = rep(comp_combinations[,1], 2),
                        mod_b = rep(comp_combinations[,2], 2),
                        fitpost_a = rep("l_postres", nrow(comp_combinations)*2),
                        fitpost_b = rep("l_postres", nrow(comp_combinations)*2), 
                        fitemp_a = rep("l_res", nrow(comp_combinations)*2),
                        fitemp_b = rep("l_res", nrow(comp_combinations)*2),
                        n_datasets = rep(n_postds, nrow(comp_combinations)*2),
                        comparison = c(rep("frob", nrow(comp_combinations)), 
                                       rep("maxdiff", nrow(comp_combinations))))

ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
starttime <- Sys.time()
cross_compare_res <- list()
cross_compare_res <- 
  lapply(c(1:nrow(comp_conditions)), function(i){
    args <- comp_conditions[i,]
    cross_compare_emp(
      mod_a = args$mod_a, 
      mod_b = args$mod_b,
      fitpost_a = eval(as.name(paste(args$fitpost_a))),
      fitpost_b = eval(as.name(paste(args$fitpost_b))), 
      fitemp_a = eval(as.name(paste(args$fitemp_a))), 
      fitemp_b = eval(as.name(paste(args$fitemp_b))), 
      n_datasets = args$n_datasets, 
      comparison = args$comparison
    )
    }
  )


stoptime <- Sys.time()-starttime    # ~16 seconds for 4950 comparisons!



stopCluster(cl)

# TODO right now I do not take into account that some samples did not work
# need to implement this, maybe as a counter


eval_res <- lapply(cross_compare_res, cross_compare_eval, plot = FALSE)
df_eval_res <- as.data.frame(do.call(rbind, eval_res))
df_eval_res <- df_eval_res %>% 
  mutate(res_a = as.numeric(res_a),
         res_b = as.numeric(res_b),
         comp = as.factor(as.character(comp))) %>% 
  group_by(comp) %>% 
  count(res_a < 5 & res_b <5)


# How many were "significant" for both
df_eval_res %>% 
  group_by(comp) %>% 
  count(res_a < 5 & res_b <5)

  



df_eval_res %>% 
  pivot_longer(cols = c(res_a, res_b), names_to = "res") %>% 
  ggplot(aes(x = value, color = comp, fill = comp))+
  geom_histogram()+
  theme_minimal()










# 
# # Compare full posterior
# test_post <- cross_compare_post(postdata_b = l_dat2_bggm, fitres_b = l_res2)
# 
# test_post %>% 
#   mutate(model_ind = as.factor(model_ind)) %>% 
#   ggplot(aes(x = frob, color = model_ind, fill = model_ind))+
#   geom_density()+
#   theme_minimal()
# 
# test_maxdiff %>% 
#         mutate(model_ind = as.factor(model_ind)) %>% 
#         ggplot(aes(x = maxdiff_null, fill = model_ind))+
#         geom_density() +
#         theme_minimal()+
#         geom_vline(aes(xintercept = max(maxdiff_emp)), col = "black",
#                    linetype = "dashed")+
#         geom_label(aes(x = max(maxdiff_emp), y = 1),
#                    label = "Emp. Maxdiff", show.legend = FALSE)+
#         labs(fill = "Model",
#              x = "Maxdiff",
#              y = "Density")+
#   ggokabeito::scale_fill_okabe_ito()

```



Another idea: for each posterior sample, generate two new datasets and obtain Frobenius norm between the two regression matrices for each sample as Null distribution. 
```{r}
# takes as input one posterior sample
# generates two new datasets, re-estimates the model and then 
# computes frobenius norm between resulting estimates
# this does not work well because there is not enough error 


frob_res <- c(rep(NA, 100))
for(i in 51:151){
  frob_res[i] <- f_post_frob(l_res[[1]]$fit$beta[,,i])
}

df_frob_res <- as.data.frame(frob_res)
df_frob_res <- na.omit(df_frob_res)
df_frob_emp <- as.data.frame(frob_emp)
df_frob_emp <- na.omit(df_frob_emp)



df_frob_res %>% 
  filter(!is.na(frob_res)) %>% 
  ggplot(aes(x = frob_res))+
  geom_density()+
  geom_vline(aes(xintercept = quantile(frob_res, 0.95), col = "red"))+
  geom_point(data = df_frob_emp, aes(x = frob_emp, y = 0), col = "blue")+
  theme_minimal()


```




For later, obtain the likelihoods of each model directly and then compare these across samples. 
```{r}

```












# Older Stuff

## Refitting approach
Refit all models to all 100 datasets. Use the internal function by Williams, modified by me.

Do I even need the intercept when all time series are standardized? He seems to ignore them. I also still need to understand what the 'predict' function does here and if it is even useful for me. The predict function uses the posterior samples to predict fitted values, so it even contains the foundation for the new simulated datasets? Not sure if this makes sense. Here we are however interested in the comparison of the graph that will actually be plotted, so just use the posterior mean of the beta coefficients for prediction.


This is not functioning at the moment because there is a new list layer to l_dat_bggm. 
```{r}
ncores = parallel::detectCores() - 8
cl = makeCluster(ncores)
registerDoParallel(cl)

# change i to n_ind or so
l_refit <- foreach(i = seq(2), .export = c("predict_pmu.var_estimate"))  %dopar% { # each model
  l_m_ref <- list()  # store for each model
  for(j in 1:n_postds){   # each simulated dataset
    l_m_ref[[j]] <- try(predict_pmu.var_estimate(object = l_res[[i]],
                             data = l_dat_bggm[[j]]))
  }
  return(l_m_ref)
} 



stopCluster(cl)
```

We use RMSE to evaluate the fit, but could also use Bayesian $R^2$ or similar stuff (maybe even the likelihood). As we get credible intervals for the predictions, we could also do something with structure recovery, so see which edges were included and which weren't if we opt for some kind of sparsity. 

```{r compute-rmse}
l_rmse <- list()
ncores = parallel::detectCores() - 4
cl = makeCluster(ncores)
registerDoParallel(cl)
l_rmse <- foreach(i = seq(n_ind)) %dopar% {  # for every model 
  df_rmse <- data.frame(iter = 1:n_ds,
                    rmse = rep(NA, n_ds),
                    model = rep(i, n_ds))
  for(j in 1:n_postds){      # for every dataset
    df_rmse[j,"rmse"] <- try(f_eval_refit(data = l_dat_bggm[[j]],
               refit = l_refit[[i]][[j]]))
  }
  return(df_rmse)
}

stopCluster(cl)
df_errors <- do.call(rbind, l_rmse)
# write_rds(df_errors, "df_errors.Rds")
```


Plot the error distribution:
```{r plot-error-dist}
df_errors %>% 
  mutate(rmse = as.numeric(rmse)) %>% 
  mutate(rmse = round(rmse, 3)) %>% 
  filter(model < 10) %>% 
  ggplot(aes(x = rmse, group = model , fill = as.factor(model), col = as.factor(model)))+
  ggdist::stat_halfeye(alpha = 0.7)+
  theme_minimal()+
  ggokabeito::scale_fill_okabe_ito()+
  ggokabeito::scale_color_okabe_ito()

```


Two ways of numerical comparison: First, treat as empirical distribution and use Kolmogorow-Smirnow. P-Values can be computed exactly or with Monte Carlo Sampling, I need to check which one makes the most sense. Apparently, the KS test (and similar tests) assume independence between the curves under consideration. 
```{r comp-kstest}
# Loop over test statistics
# Baseline is model 1
err1 <- df_errors$rmse[df_errors$model == 1]
df_ks_res <- data.frame(model = rep(NA, n_mod),
                        statistic = rep(NA, n_mod),
                        pval = rep(NA, n_mod))
options(scipen=999)

# Filter model that did not converge, have to do this more principled later on
df_errors <- df_errors %>% 
  mutate(rmse = as.numeric(rmse)) %>% 
  filter(!is.na(rmse))

for(m in 2:n_mod){
  if(m != 75){
  err_alt <- df_errors$rmse[df_errors$model == m]
  tmp <- stats::ks.test(x = err1,
                 y = err_alt,
                 alternative = "greater")
  df_ks_res[m,"model"] <- m
  df_ks_res[m, "statistic"] <- tmp$statistic[[1]]
  df_ks_res[m, "pval"] <- round(tmp$p.value, 5)
  }

}

# Still too many false positives?
# maybe I should actually test one-sided, because some of the models
# actually fit better than the reference model
sum(df_ks_res$pval < 0.001, na.rm = TRUE)



```

Second, estimate density, treat as empirical distribution and calculate Jenson-Shannon-Divergence (which is symmetrical, KL-Divergence is not).
The exact method for estimating the density should not matter too much, as the distribution of errors should roughly follow a normal distribution. For now, just use the density approach in the `stats` package with a Gaussian kernel. 1-JSD is a similarity metric. 
```{r}

# compute for whole dataset
jsd_res <- f_comp_jsd(df = df_errors, n = 100)

jsd_res %>% 
  ggplot(aes(x = jsd))+
  geom_density()+
  theme_minimal()


```


Another idea: compute something like absolute difference between network results, as van Borkulo et al. did it. 
```{r}

```





# Concatenating Time Series
Another idea is based on Williams & Mulder (2020). Instead of comparing the posterior predictive estimations of two datasets directly, we could concatenate two time series under the null hypothesis that they originate from the same data-generating process. We could then compare the posterior predictive results from these concatenated time series to either a distribution from an individual time series or just a single test statistic. This is also comparable to Zhang, Templin & Mintz (2022). 

```{r concatenate-ts}
# time series need to be standardized before concatenation
# we also need to assume stationarity 
# first just take the first two time series here
conc_12 <- rbind(l_dat[[1]]$Y, l_dat[[3]]$Y)

# delete first entry of second time series to create gap
# conc_12[nrow(conc_12)/2+1,] <- c(NA, NA, NA, NA, NA, NA)

# delete multiple entries in the middle of the time series to create gap
conc_12[197:201,] <- c(rep(NA, 6))

# Estimate new model on concatenated dataset
# Fit the model
rho_sd <- 0.5
beta_sd <- 1
seed <- 2022
n_iter <- 5000

# estimate model on concatenated dataset
res_conc12 <- BGGM::var_estimate(conc_12,
                                   rho_sd = rho_sd,
                                   beta_sd = beta_sd,
                                   iter = n_iter,
                                   progress = FALSE,
                                   seed = seed)

# results are very different compared to just one model
res_conc12$beta_mu
l_res[[1]]$beta_mu
l_res[[2]]$beta_mu
t(graph$beta)


```





Just a quick check on how well parameters are recovered: 
```{r}
test <- list()
for(i in 1:length(l_res)){
  test[[i]] <- l_res[[i]]$beta_mu
}
a_test <- array(unlist(test), c(6,6,100))

# means across refit samples
rowMeans(a_test, dims = 2)
# comparison with ground truth
t(graph$beta)
```




















