---
title: "var-compare-empirical-example"
author: "Björn Siepe"
date: "2023-01-30"
output: html_document
---

We use data from Fisher et al. (2017), downloaded from https://github.com/jmbh/EmotionTimeSeries/blob/master/DataClean/Fisher2017/data_Fisher2017.RDS. 

# Preparation and Data Cleaning
```{r}
library(BGGM)
library(qgraph)
library(tidyverse)
data <- readRDS("data_Fisher2017.RDS")



# Number of observations per model
n_obs <- data %>% 
  count(subj_id)

# Use 6 items
short_data <- data %>% 
  # dplyr::filter(subj_id %in% rel_ids) %>% 
  dplyr::select(subj_id, content, worried, anhedonia, positive, fatigue, accepted) %>% 
  group_by(subj_id) %>% 
  mutate(tp = row_number()) %>% 
  ungroup() %>% 
  split(.$subj_id)


short_data <- data %>% 
  # dplyr::filter(subj_id %in% rel_ids) %>% 
  dplyr::select(subj_id, reassure, down, anhedonia, enthusiastic, hopeless, accepted) %>% 
  group_by(subj_id) %>% 
  mutate(tp = row_number()) %>% 
  ungroup() %>% 
  split(.$subj_id)



```


## Detrending

TODO: Double check if this worked
```{r}
# Relevant variables
rel_vars <- c("content", "worried", "anhedonia", "positive", "fatigue", "accepted")
rel_vars <- c("reassure", "down", "anhedonia", "enthusiastic", "hopeless", "accepted")

data_detrend <- lapply(short_data, function(x){
  for (v in 1:length(rel_vars)){
  # Respektive Variable auf die Zeit regressieren
  lm_form <- as.formula(paste0(rel_vars[v], "~ tp"))
  # lineares Modell rechnen
  lm_res <- summary(lm(lm_form, data = x))
  # wenn der Zeittrend signifikant ist, detrenden wir mit den Residuen
  # [,4] greift auf die Spalte der p-Werte zu
  # [2] auf den p-Wert des Regressionsgewichts des Datums
  if(lm_res$coefficients[,4][2] < 0.05){
    print(paste0("Detrende Variable: ", rel_vars[v]))
    x[!is.na(x[rel_vars[v]]),rel_vars[v]] <- residuals(lm_res)
  }
  
}
return(x)
})





```




Fit all models
```{r}
rho_prior = 0.5
beta_prior = 1
iterations = 15000
seed = 2022

l_fits <- list()
l_fits <- lapply(data_detrend, function(x){
  tryCatch(BGGM::var_estimate(x[,-c(1, 8)],      # delete id column and tp column for fitting
                     rho_sd = rho_prior,
                     beta_sd = beta_prior,
                     iterations = iterations, 
                     seed = seed), error = function(e) NA)
})

# delete nonconverged
# l_fits <- l_fits[sapply(l_fits, is.list)]
# get param names
param_names <- BGGM::convergence(l_fits[[1]], print_names = TRUE)

# Trace Plots
BGGM::convergence(l_fits[[1]], type = "trace",  param = "reassure--accepted")

# ACF
BGGM::convergence(l_fits[[1]], type = "acf", param = "down--enthusiastic")


pdf("convergence_empirical.pdf")
for(i in 1:10){
  for(n in param_names){

  print(BGGM::convergence(l_fits[[1]], type = "acf", param = n))
  
}
}
dev.off()


```


## Plot all networks

```{r}
plot_net <- function(fit_obj){
  par(mfrow=c(1,2))
  qgraph::qgraph(fit_obj$beta_mu, title = "Temporal", theme = "colorblind", layout = "circle")
  qgraph::qgraph(fit_obj$pcor_mu, title = "Contemporaneous", theme = "colorblind", layout = "circle")
}


```






Temporary new function for post distance within without kappa and compare_var

TODO just write summary method for compare function
```{r}
post_distance_within_nokap <- function(post, 
                                 comp,
                                 pred,         # posterior predictive?
                                 draws = 1000){
  
  # storage
  dist_out <- list()
  
  
  # for posterior predictive approach
  if(isTRUE(pred)){
    # define the distance function based on comp
    distance_fn_beta <- switch(comp,
                               frob =   {function(x, y, mod_one, mod_two) norm(x$fit[[mod_one]]$beta_mu-y$fit[[mod_two]]$beta_mu, type = "F")},
                               maxdiff = {function(x, y, mod_one, mod_two) max(abs((x$fit[[mod_one]]$beta_mu-y$fit[[mod_two]]$beta_mu)))},
                               l1 = {function(x, y, mod_one, mod_two) sum(abs((x$fit[[mod_one]]$beta_mu-y$fit[[mod_two]]$beta_mu)))}
    )
    distance_fn_pcor <- switch(comp,
                               frob = {function(x, y, mod_one, mod_two) norm(x$fit[[mod_one]]$pcor_mu-y$fit[[mod_two]]$pcor_mu, type = "F")},
                               maxdiff = {function(x, y, mod_one, mod_two) max(abs((x$fit[[mod_one]]$pcor_mu-y$fit[[mod_two]]$pcor_mu)))},
                               l1 = {function(x, y, mod_one, mod_two) sum(abs((x$fit[[mod_one]]$pcor_mu-y$fit[[mod_two]]$pcor_mu)))}
    )

    
    
    
    # Obtain number of models
    n_mod <- length(post$fit)
    
  }

  
  # for posteriors of empirical models
  if(isFALSE(pred)){
    # define the distance function based on comp
    # draw from all posterior samples
    
    # Convert Kappas to Pcors

    
    
    distance_fn_beta <- switch(comp,
                               frob =   {function(x, y, mod_one, mod_two) norm(x$fit$beta[,,mod_one]-y$fit$beta[,,mod_two], type = "F")},
                               maxdiff = {function(x, y, mod_one, mod_two) max(abs((x$fit$beta[,,mod_one]-y$fit$beta[,,mod_two])))},
                               l1 = {function(x, y, mod_one, mod_two) sum(abs((x$fit$beta[,,mod_one]-y$fit$beta[,,mod_two])))}
    )
    distance_fn_pcor <- switch(comp,
                               frob = {function(x, y, mod_one, mod_two) norm(x$fit$pcors[,,mod_one]-y$fit$pcors[,,mod_two], type = "F")},
                               maxdiff = {function(x, y, mod_one, mod_two) max(abs((x$fit$pcors[,,mod_one]-y$fit$pcors[,,mod_two])))},
                               l1 = {function(x, y, mod_one, mod_two) sum(abs((x$fit$pcors[,,mod_one]-y$fit$pcors[,,mod_two])))}
    )

    # Obtain number of posterior samples
    n_mod <- dim(post$fit$beta)[3]
    
  }
  
  
  
  ## Draw two random models
  # delete burn-in iterations (to 50)
  # n_mod <- n_mod[-c(1:50)]
  
  # TODO: actually, "samples" would be more fitting here than "models"
  # "model" is still a residue from posterior predictive approach
  # Draw models spaced apart so that we don't have autocorrelation from sampling
  mod_pairs <- array(NA, dim = c(2, draws))
  # draw from first half of samples
  mod_pairs[1,1:(draws)] <- seq(51, draws+50, by = 1)
  
  # draw from second half of samples
  mod_pairs[2,1:(draws)] <- seq((n_mod/2)+51, (n_mod/2)+50+(draws), by = 1)
  
  # mod_pairs <- replicate(draws, sample(1:n_mod, size = 2, replace = TRUE))
  
for(i in seq(draws)){
  # storage
  dist_out[[i]] <- list()
  mod_one <- mod_pairs[1,i]
  mod_two <- mod_pairs[2,i]
  
# if mod_one and mod_two are equal, redraw
  if(mod_one == mod_two){
    mod_two <- sample(1:n_mod, size = 1)
}
  
  ## Check if estimation worked
  # Should be unneccessary if non-converged attempts were deleted
  if(isTRUE(pred)){
    if(!is.list(post$fit[[mod_one]]) | !is.list(post$fit[[mod_two]])){
      beta_distance <- NA
      pcor_distance <- NA
      stop("Not a list.")
      
      
    } 
    # if both elements are lists
    else{
      beta_distance <- distance_fn_beta(post, post, mod_one, mod_two)
      pcor_distance <- distance_fn_pcor(post, post, mod_one, mod_two)

    }  
  }
  
  if(isFALSE(pred)){
    if(!is.list(post) | !is.list(post)){
      beta_distance <- NA
      pcor_distance <- NA

      stop("Not a list.")
      
    } 
    # if both elements are lists
    else{
      beta_distance <- distance_fn_beta(post, post, mod_one, mod_two)
      pcor_distance <- distance_fn_pcor(post, post, mod_one, mod_two)

    }  
  }
  



  dist_out[[i]]$comp <- comp
  dist_out[[i]]$mod_one <- mod_one
  dist_out[[i]]$mod_two <- mod_two
  dist_out[[i]]$beta <- beta_distance
  dist_out[[i]]$pcor <- pcor_distance  

  
} # end for loop  
  out <- do.call(rbind, dist_out)
  out <- as.data.frame(out)
  
  
  return(out)
}



compare_var <- function(fit_a, 
                        fit_b, 
                        cutoff = 5,           # percentage level of test
                        dec_rule = "OR",
                        n_draws = 1000,
                        comp = "frob"){
  
  ## Create reference distributions for both models
  ref_a <- post_distance_within_nokap(fit_a, comp = comp, pred = FALSE, draws = n_draws)
  ref_b <- post_distance_within_nokap(fit_b, comp = comp, pred = FALSE, draws = n_draws)
  
  ## Empirical distance
    # Compute empirical distance as test statistic
    if(comp == "frob"){
      normtype = "F"
      # Compute Distance of empirical betas between a and b
      emp_beta <- tryCatch(norm(fit_a$beta_mu - fit_b$beta_mu, type = normtype), error = function(e) {NA})
      
      # Compute Distance of empirical pcors between a and b
      emp_pcor <- tryCatch(norm(fit_a$pcor_mu - fit_b$pcor_mu, type = normtype), error = function(e) {NA})
      
    }
    
    if(comp == "maxdiff"){
      # Compute maxdiff of empirical betas between a and b
      emp_beta <- tryCatch(max(abs(fit_a$beta_mu - fit_b$beta_mu)), error = function(e) {NA})
      
      # Compute maxdiff of empirical pcors between a and b
      emp_pcor <- tryCatch(max(abs(fit_a$pcor_mu - fit_b$pcor_mu)), error = function(e) {NA})

    }
    
    if(comp == "l1"){
      # Compute l1 of empirical betas between a and b
      emp_beta <- tryCatch(sum(abs(fit_a$beta_mu - fit_b$beta_mu)), error = function(e) {NA})
      
      # Compute l1 of empirical pcors between a and b
      emp_pcor <- tryCatch(sum(abs(fit_a$pcor_mu - fit_b$pcor_mu)), error = function(e) {NA})

    }
  ## Combine results
    res_beta <- data.frame(null = c(unlist(ref_a[["beta"]]), unlist(ref_b[["beta"]])),
                              mod = c(rep("mod_a", n_draws), rep("mod_b", n_draws)),
                              emp = rep(emp_beta, n_draws*2),
                              comp = rep(comp, n_draws*2))
    
    
    res_pcor <- data.frame(null = c(unlist(ref_a[["pcor"]]), unlist(ref_b[["pcor"]])),
                              mod = c(rep("mod_a", n_draws), rep("mod_b", n_draws)),
                              emp = rep(emp_pcor, n_draws*2),
                              comp = rep(comp, n_draws*2))
  
  ## Implement decision rule "OR"
  if(dec_rule == "OR"){
    suppressWarnings(sig_beta <- res_beta %>% 
      group_by(mod) %>% 
      summarize(sum_larger = sum(null > emp)) %>% 
      summarize(sig = ifelse(sum_larger < cutoff * (n_draws/100), 1, 0)) %>% 
      summarize(sig_decision = sum(sig)) %>% 
      pull(sig_decision))
    
    suppressWarnings(larger_beta <- res_beta %>% 
      group_by(mod) %>% 
      summarize(sum_larger = sum(null > emp))) %>% 
      pull(sum_larger)
    
    suppressWarnings(sig_pcor <- res_pcor %>% 
      group_by(mod) %>% 
      summarize(sum_larger = sum(null > emp)) %>% 
      summarize(sig = ifelse(sum_larger < cutoff * (n_draws/100), 1, 0)) %>% 
      summarize(sig_decision = sum(sig)) %>% 
      pull(sig_decision))
    
    suppressWarnings(larger_pcor<- res_pcor %>% 
      group_by(mod) %>% 
      summarize(sum_larger = sum(null > emp))) %>% 
      pull(sum_larger)
    
      
  }
  l_res <- list(sig_beta = sig_beta,
                sig_pcor = sig_pcor,
                res_beta = res_beta,
                res_pcor = res_pcor,
                emp_beta = emp_beta,
                emp_pcor = emp_pcor)

  return(l_res)
  

  
}

# Plotting method
# THIS IS ONLY TEMPORARY!!!!!
plot.compare_var <- function(compres,
                             ...){
  require(ggplot2)
  require(cowplot)
  # create df
  # dat <- rbind(compres$res_beta, compres$res_pcor)
  
  
  
  # Plotting
  plt_beta <- ggplot(compres$res_beta, 
                aes(x = null, fill = mod))+
    geom_density(alpha = .7)+
    theme_classic()+
    ggokabeito::scale_fill_okabe_ito()+
    geom_vline(aes(xintercept = compres$emp_beta), 
               col = "red", lty = 1, linewidth = .75)+
    labs(title = "Temporal")
  
  plt_pcor <- ggplot(compres$res_pcor, 
                aes(x = null, fill = mod))+
    geom_density(alpha = .7)+
    theme_classic()+
    ggokabeito::scale_fill_okabe_ito()+
    geom_vline(aes(xintercept = compres$emp_pcor), 
               col = "red", lty = 1, linewidth = .75)+
    labs(title = "Contemporaneous")
  
  leg <- get_legend(plt_beta)
  
  # Plot
  plt_tmp <- cowplot::plot_grid(plt_beta + theme(legend.position = "none"),
                            plt_pcor + theme(legend.position = "none"))

  # Add legend
  plt <- plot_grid(plt_tmp, leg, rel_widths = c(3, .4))
  plt
  
}





```







Test across all participants
```{r}
fit_grid <- expand.grid(fit_a = as.numeric(names(l_fits)), fit_b = as.numeric(names(l_fits)))
l_comps <- list()
l_comps <- pbapply::pblapply(c(1:nrow(fit_grid)), function(x){
  
  a <- fit_grid$fit_a[x]
  b <- fit_grid$fit_b[x]
  
  if(is.list(l_fits[[a]]) & is.list(l_fits[[b]])){
    compare_var(l_fits[[a]],l_fits[[b]], comp = "l1")
  }
  
})
comps <- do.call(rbind.data.frame, l_comps)
# delete nonconverged attempts
r_nonconv <- which(sapply(l_comps, function(x) length(x) == 0))
# fit_grid_conv <- fit_grid[-r_nonconv,]

df_comps <- cbind(comps, fit_grid)


```

Extract interesting cases
```{r}
# Find interesting cases with similar amount of observations
# nonsignificant 
df_comps %>% 
  filter(sig_beta == 0 & sig_pcor  == 0) %>% 
  filter(fit_a != fit_b) %>% 
  left_join(n_obs, by = join_by(fit_a == subj_id)) %>% 
  left_join(n_obs, by = join_by(fit_b == subj_id), suffix = c("_a", "_b")) %>% 
  mutate(diff_n = abs(n_a - n_b)) %>% 
  arrange(diff_n)


# Both significant
df_comps %>% 
  filter(sig_beta > 1 & sig_pcor  > 1) %>% 
  filter(fit_a != fit_b) %>% 
  left_join(n_obs, by = join_by(fit_a == subj_id)) %>% 
  left_join(n_obs, by = join_by(fit_b == subj_id), suffix = c("_a", "_b")) %>% 
  mutate(diff_n = abs(n_a - n_b)) %>% 
  arrange(diff_n) %>% View()


```







Visualize distributions of empirical differences
```{r}
df_comps %>% 
  filter(fit_a != fit_b) %>% 
  pivot_longer(cols = c("emp_beta", "emp_pcor"), names_to = "mat") %>% 
  ggplot(aes(x = value, fill = as.factor(mat))) +
  geom_density()
```




# Example A: Evidence for differences
27 and 3
```{r}
compare_var(l_fits[[8]], l_fits[[27]])
plot_net(l_fits[[8]])
plot_net(l_fits[[27]])


# Visualize differences
it_diff <- which(df_comps$fit_a == 8 & df_comps$fit_b == 27)
plot.compare_var(l_comps[[it_diff]])

```






# Example B: No evidence for differences
8 and 29
```{r}
compare_var(l_fits[[8]], l_fits[[29]])

plot_net(l_fits[[8]])
plot_net(l_fits[[29]])


# Visualize Differences
# Find iteration number
it_nodiff <- which(df_comps$fit_a == 8 & df_comps$fit_b == 29)

plot.compare_var(l_comps[[it_nodiff]])


```




