---
title: "posterior-predictive"
author: "Björn Siepe"
output: html_document
---


# Preparation
Idea is to use a posterior predictive approach to create reference distributions.
All of this does not work with the standard version of BGGM! I need to obtain the Kappas from the sampler. Hence, we use BGGMmod.
```{r}
library(BGGMmod)
library(foreach)
library(tidyverse)
library(doParallel)
library(here)
source("aux_funs.R")
```


# Functions
This is taken from an earlier approach
```{r}
# Sim from posterior ------------------------------------------------------
#' Simulate from Posterior Samples
#' This function simulates a specified number of datasets from the posterior
#' of a given model. Uses the graphicalVARsim function from the graphicalVAR
#' package to generate data. 
#' @param fitobj BGGM fit object containing all posterior samples
#' @param n_datasets Number of datasets to create
#' @param n Number of individuals
#' @param tp Number of timepoints
#' @param iterations Number of iterations used in BGGM sampling
#' @param means Mean vector
#' @param convert_bggm DEPRECATED: Should results be converted to BGGM List format?
#'
#' @return List of datasets in dataframe format. 
#' @export

sim_from_post <- function(fitobj, 
                                   n_datasets, 
                                   tp,
                                   iterations,
                                   seed,
                                   burnin = 500, 
                                   expected = FALSE, # expected values or samples   
                                   means = 0,
                                   convert_bggm = FALSE){

  # browser()
  
  # If only one model was fitted, fitobj is not a list
  beta <- fitobj$fit$beta[,,(burnin+1):iterations]
  kappa <- array(
    apply(fitobj$fit$Sigma[,,(burnin+1):iterations], 3, solve),
    dim = dim(fitobj$fit$Sigma[,,(burnin+1):iterations]))
  kappa_mu <- apply(kappa, c(1,2), mean)

  if(isFALSE(expected)){
  # get random posterior samples
  smp <- sample(iterations, size = n_datasets)
  dat <- lapply(seq(n_datasets), function(i) {
  # Needs transposing of beta matrix!
    try(as.data.frame(
      graphicalVAR::graphicalVARsim(nTime = tp,
                                  beta = t(beta[,,smp[i]]),
                                  kappa = kappa[,,smp[i]],
                                  mean = means))) 
})
  }
  if(isTRUE(expected)){
    # get kappa_mu
    
   dat <- lapply(seq(n_datasets), function(i) {
      # get random posterior sample
      # Needs transposing of beta matrix!
      try(as.data.frame(
        graphicalVAR::graphicalVARsim(nTime = tp,
                                      beta = t(fitobj$beta_mu),
                                      kappa = kappa_mu,
                                      mean = means)))
    })
  }

    dat
}
```


# Example

Fit models on example data:
```{r}
# Use networks from simulation study
l_changed_graphs <-readRDS(here("data/l_changed_graphs_0305.RDS"))

n_tp <- 200

# Simulate two datasets
net_1a <- graphicalVAR::graphicalVARsim(n_tp,
                                       beta = l_changed_graphs$graph4$truegraph$beta,
                                       kappa = l_changed_graphs$graph4$truegraph$kappa)
net_1b <- graphicalVAR::graphicalVARsim(n_tp,
                                       beta = l_changed_graphs$graph4$truegraph$beta,
                                       kappa = l_changed_graphs$graph4$truegraph$kappa)

net_2 <- graphicalVAR::graphicalVARsim(n_tp,
                                       beta = l_changed_graphs$graph4$const0.05$beta,
                                       kappa = l_changed_graphs$graph4$const0.05$kappa)


net_3 <- graphicalVAR::graphicalVARsim(n_tp,
                                       beta = l_changed_graphs$graph4$const0.15$beta,
                                       kappa = l_changed_graphs$graph4$const0.15$kappa)

# Estimate networks
r_net_1a <- BGGMmod::var_estimate(as.data.frame(net_1a),
                            rho_sd = 0.25, 
                            beta_sd = 0.5,
                            iter = 50000)
r_net_1b <- BGGMmod::var_estimate(as.data.frame(net_1b),
                            rho_sd = 0.25, 
                            beta_sd = 0.5,
                            iter = 50000)
r_net_2 <- BGGMmod::var_estimate(as.data.frame(net_2),
                            rho_sd = 0.25, 
                            beta_sd = 0.5,
                            iter = 50000)

r_net_3 <- BGGMmod::var_estimate(as.data.frame(net_3),
                            rho_sd = 0.25, 
                            beta_sd = 0.5,
                            iter = 50000)


# Check if I can get the kappas
# Invert covariance matrix of residuals to obtain precision matrix
r_net_1a$fit$kappa <- array(apply(r_net_1a$fit$Sigma, 3, solve), 
                                       dim = dim(r_net_1a$fit$Sigma))
            
# Calculate mean of kappa
r_net_1a$kappa_mu <- apply(r_net_1a$fit$kappa, c(1,2), mean)
```


## Compute posterior predictives

```{r}
sim_1a <- sim_from_post(r_net_1a, 
                        expected = TRUE,
                                 10,
                                 tp = n_tp, 
                                 iterations = 50000, 
                                 seed = 123)
sim_3 <- sim_from_post(r_net_3, 
                                 10,
                                 tp = n_tp, 
                                 iterations = 50000, 
                                 seed = 123)


```


# Fit on posterior predictives

Reuse the old function here: 
```{r}
fit_var_parallel_revision <- function(data, 
                                     n,         # number of individuals
                                     nds,       # number of datasets
                                     rho_prior, 
                                     beta_prior,
                                     seed,
                                     iterations,
                                     get_kappa = FALSE,
                                     posteriorsamples = FALSE,
                                     multigroup = FALSE,
                                     pruneresults = FALSE, 
                                     summarize_post = TRUE, # summarize posterior samples into intervals 
                                     cred_int = 0.95,       # credible interval for posterior summary
                                     select = FALSE,       # apply selection based on CI, currently only supported for non single dataset fitting
                                     save_files = FALSE,
                                     dgp_name = NULL){     # option to return as .rds
  
  # browser()
  
  if(n != length(data)){
    warning("The n provided does not match the number of available data frames")
  }
  require(doParallel)

  # reproducible parallelization
  doRNG::registerDoRNG(seed)
  
  
  # Input checks
  if(isTRUE(select) & isTRUE(pruneresults)){
    stop("Using select and pruneresults at the same time is not supported.")
  }
  

  if(isFALSE(posteriorsamples) & isFALSE(multigroup)){
    print("Fitting to raw data")
    fit <- foreach(i = seq(nds), .packages = "BGGMmod", .export = "sim_select") %dopar% {

      fit_ind <- list()
      if(is.list(data[[i]]$data) | is.numeric(data[[i]]$data)){
        fit_ind <- tryCatch({BGGMmod::var_estimate(as.data.frame(data[[i]]$data),
                                                rho_sd = rho_prior,
                                                beta_sd = beta_prior,
                                                iter = iterations,
                                                progress = FALSE,
                                                seed = seed)}, error = function(e) NULL)
        
        
        # Delete irrelevant matrices
        if(is.list(fit_ind)){
          fit_ind$fit$fisher_z <- NULL
        }
        
        
        if(isTRUE(get_kappa)){
          # check if fitting worked
          if(is.list(fit_ind)){
            # Invert covariance matrix of residuals to obtain precision matrix
            fit_ind$fit$kappa <- array(apply(fit_ind$fit$Sigma, 3, solve), 
                                       dim = dim(fit_ind$fit$Sigma))
            
            # Calculate mean of kappa
            fit_ind$kappa_mu <- apply(fit_ind$fit$kappa, c(1,2), mean)
            
          }

        }
        
        # prune results for comparison purposes
        if(isTRUE(pruneresults) & is.list(fit_ind)){
          # beta <- fit_ind$fit$beta
          # kappa <- fit_ind$fit$kappa
          beta_mu <- fit_ind$beta_mu 
          pcor_mu <- fit_ind$pcor_mu
          # kappa_mu <- fit_ind$kappa_mu
          args <- data[[i]]$args
          fit_ind <- list()
          fit_ind$beta_mu <- beta_mu
          fit_ind$pcor_mu <- pcor_mu
          fit_ind$kappa_mu <- NA
          fit_ind$args <- args
          # fit_ind$fit$beta <- beta
          # fit_ind$fit$kappa <- kappa

        } # end if isTRUE 
        
        # Select option
        if(isTRUE(select) & is.list(fit_ind)){
          sel <- sim_select(fit_ind)
          if(isTRUE(summarize_post)){
            cred_interval <- summarize_post(fit_ind, cred = cred_int)
          }
          fit_ind <- list()
          fit_ind <- stats::setNames(sel, names(sel))
          fit_ind$args <- data[[i]]$args
          if(isTRUE(summarize_post)){
            fit_ind$cred_interval <- cred_interval
          }
          
          
        } # end isTRUE select
        
        if(isFALSE(select) & isTRUE(summarize_post) & is.list(fit_ind)){
          beta_mu <- fit_ind$beta_mu 
          pcor_mu <- fit_ind$pcor_mu
          # kappa_mu <- fit_ind$kappa_mu
          args <- data[[i]]$args
          cred_interval <- summarize_post(fit_ind, cred = cred_int)
          fit_ind <- list()
          fit_ind$beta_mu <- beta_mu
          fit_ind$pcor_mu <- pcor_mu
          fit_ind$kappa_mu <- NA
          fit_ind$cred_interval <- cred_interval
          fit_ind$args <- args
          
        }
        

        
      } # end if is.list
      # else fit_ind <- NA
      
      return(fit_ind)  
    } # end foreach
    # Cut away nonconverged attempts
    # only for non-select
    # if(isFALSE(select)){
    #   lapply(fit, function(x){
    #     if(length(x$fit) == 0){
    #       warning("Some models did not converge!")}
    #   })
    #   fit <- fit[!sapply(fit, function(x) length(x$fit) == 0)]
    #   
    #   
    #   # Return list with desired length
    #   fit <- fit[c(1:n)]
    # }


    
    if(isFALSE(save_files)){
      return(fit)
      
    }
    # If outputs should be saved as RDS
    if(isTRUE(save_files)){
      saveRDS(fit, file = here::here(paste0("data/compare_sim_fits/fit_",dgp_name, "_", data[[1]]$args$dgp, "_", data[[1]]$args$tp,".RDS")))
      
    }
    
    
  } # end isFALSE(posteriorsamples)
  
  
  # if we fit the data on samples generated from the posterior
  if(isTRUE(posteriorsamples)){
    print("Fitting to posterior samples")
    
    # counter for converged models 
    m <- list()
    # counter for attempted models
    c <- list()
    
    
    # loop across individuals
    fit <- foreach(i = seq(n), .packages = "BGGMmod") %dopar% {
      # Counter for converged models
      m[[i]] <- 0
      # Counter for estimated models
      c[[i]] <- 0
      fit <- list()
      # loop across datasets
        if(m[[i]] >= 100){
          break 
        }
        
        fit_ind <- list()
        if(is.list(data[[i]])){
          fit_ind <- tryCatch({BGGMmod::var_estimate(data[[i]],
                                                  rho_sd = rho_prior,
                                                  beta_sd = beta_prior,
                                                  iter = iterations,
                                                  progress = FALSE,
                                                  seed = seed)}, error = function(e) NULL)
          # Add to counter for estimated models
          c[[i]] <- c[[i]]+1
          
          # check if fitting worked
          if(is.list(fit_ind)){
            m[[i]] <- m[[i]]+1
            # print(m[[i]])
            
            
            if(isTRUE(get_kappa)){
              # Invert covariance matrix of residuals to obtain precision matrix
              fit_ind$fit$kappa <- array(apply(fit_ind$fit$Sigma, 3, solve), 
                                         dim = dim(fit_ind$fit$Sigma))
              # Calculate mean of kappa
              fit_ind$kappa_mu <- apply(fit_ind$fit$kappa, c(1,2), mean)
              
            }
            
            
            # prune results for comparison purposes
            # When fitting to posterior data, we no longer need 
            # raw kappa/beta matrizes
            if(isTRUE(pruneresults)){
              # kappa <- fit_ind$fit$kappa
              # beta <- fit_ind$fit$beta
              beta_mu <- fit_ind$beta_mu 
              kappa_mu <- fit_ind$kappa_mu
              pcor_mu <- fit_ind$pcor_mu
              n_attempts <- c[[i]]
              fit_ind <- list()
              # fit_ind$fit <- list()
              fit_ind$beta_mu <- beta_mu
              fit_ind$kappa_mu <- kappa_mu
              fit_ind$pcor_mu <- pcor_mu
              fit_ind$n_attempts <- n_attempts
              # fit_ind$fit$beta <- beta
              # fit_ind$fit$kappa <- kappa
              
            } 
            
            
          }    # end is.list(fit_ind)
          
          
        } # end is.list(data[[i]])  
        
        
      
      return(fit_ind)
      
    }
    return(fit)
    
  } # end isTRUE posteriorsamples
  if(isTRUE(multigroup)){
    print("Fitting to multigroup posterior samples")
    
    # counter for converged models 
    m <- list()
    # counter for attempted models
    c <- list()
    
    fit <- list()
    
    # Progressbar
    pb <- utils::txtProgressBar(0, nds, style = 3)
    
    # loop across samples
    fit <- foreach(i = seq(nds), .packages = "BGGMmod") %dopar% {
      utils:: setTxtProgressBar(pb, i)
      
      # TODO reimplement!
      # # Counter for converged models
      # m[[i]] <- 0
      # # Counter for estimated models
      # c[[i]] <- 0
      fit_ind <- list()
      # loop across groups
      for(d in seq(n)) {
        # if(m[[i]] >= 100){
        #   break 
        # }
        
        if(is.list(data[[i]])){
          if(is.list(data[[i]][[d]])){
            fit_ind[[d]] <- tryCatch({BGGMmod::var_estimate(as.data.frame(data[[i]][[d]]$data),
                                                         rho_sd = rho_prior,
                                                         beta_sd = beta_prior,
                                                         iter = iterations,
                                                         progress = FALSE,
                                                         seed = seed)}, error = function(e) NA)
            # # Add to counter for estimated models
            # c[[i]] <- c[[i]]+1
            
            # check if fitting worked (length condition needed when first d iteration
            # fails and list is empty)
            if(length(fit_ind) > 0){
              if(is.list(fit_ind[[d]])){
                # m[[i]] <- m[[i]]+1
                # print(m[[i]])
                
                
                if(isTRUE(get_kappa)){
                  # Invert covariance matrix of residuals to obtain precision matrix
                  fit_ind[[d]]$fit$kappa <- array(apply(fit_ind[[d]]$fit$Sigma, 3, solve), 
                                                  dim = dim(fit_ind[[d]]$fit$Sigma))
                  # Calculate mean of kappa
                  fit_ind[[d]]$kappa_mu <- apply(fit_ind[[d]]$fit$kappa, c(1,2), mean)
                  
                }
                
                
                # prune results for comparison purposes
                # When fitting to posterior data, we no longer need 
                # raw kappa/beta matrizes
                if(isTRUE(pruneresults)){
                  # kappa <- fit_ind[[d]]$fit$kappa
                  # beta <- fit_ind[[d]]$fit$beta
                  beta_mu <- fit_ind[[d]]$beta_mu 
                  kappa_mu <- fit_ind[[d]]$kappa_mu
                  pcor_mu <- fit_ind[[d]]$pcor_mu
                  # n_attempts <- c[[i]]
                  fit_ind[[d]] <- list()
                  # fit_ind[[d]]$fit <- list()
                  fit_ind[[d]]$beta_mu <- beta_mu
                  fit_ind[[d]]$kappa_mu <- kappa_mu
                  fit_ind[[d]]$pcor_mu <- pcor_mu
                  # fit_ind[[d]]$n_attempts <- n_attempts
                  # fit_ind[[d]]$fit$beta <- beta
                  # fit_ind[[d]]$fit$kappa <- kappa
                  
                } # end isTRUE(pruneresults)
                
                
              }    # end is.list(fit_ind)
            }
            
            
            
          } # end is.list(data[[i]])  
        }
        
        
        
      } # end loop across groups 
      
      return(fit_ind)
      
    } # end foreach 
    return(fit)
    
  } # end isTRUE multigroup
  
  

  
}  
```



```{r}
ncores = 8
cl = makeCluster(ncores)
clusterExport(cl = cl, "summarize_post")
registerDoParallel(cl)
# Fit models on posterior predictives
post_pred_fit <- fit_var_parallel_revision(sim_3,
                          rho_prior = 0.25,
                          beta_prior = 0.5,
                          iterations = 50000,
                          n = 10,
                          nds = 1,
                          seed = 35037,
                          get_kappa = FALSE, 
                          posteriorsamples = TRUE,
                          summarize_post = FALSE,
                          pruneresults = FALSE,
                          save_files = FALSE,
                          multigroup = FALSE,
                          select = FALSE)

stopCluster(cl)
```



# Compute reference distribution from posterior predictive fits
Now we can compute a reference distribution from these 100 fits. To do so, we create comparison distributions between a random sample of 100 pairs. 
```{r}
compare_gvar_between(post_pred_fit[[1]],
                     post_pred_fit[[2]])



```



