---
title: "simulation-2-revision-meanpost"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

# Prep
Background: As an extension to the overlap simulation, we here try to revamp the idea that is already implemented in the paper, but we take the mean of posterior distances instead of the posterior distance of the mean. 

```{r}
library(tidyverse)
library(graphicalVAR)
library(doParallel)
library(doRNG)         
library(mgm)
library(mlVAR)
library(BGGM)
library(reshape2)      
library(mvtnorm)       
library(stats)     
library(here)
source(here("aux_funs.R"))
library(ggokabeito)
library(Matrix)
library(rrapply)       
library(ggh4x)
library(gt)
library(gtExtras)
here::i_am("var-compare.Rproj")


seed = 2022
set.seed(seed)
```

Sim conditions
```{r}
# Simulation conditions
n_ind <- 100 # number of individuals(so models to create) 
n_tp <- c(50,100,200,400, 1000) # number of timepoints
n_postds <- 120 # number of posterior datasets
seed <- 2022
dgp_names <- c("graph1", "graph2", "graph3", "graph4", "graph5")
```


# Implement comparison

```{r}
compare_posterior_mean <- function(comp_obj, 
                              equiv_range_beta = 0,
                              equiv_range_pcor = 0,
                              # Should within posterior uncertainty of A and B be combined?
                              combine_posteriors = TRUE,
                              nvar = 6) {
  
  # browser()
  
  overlap_df <- data.frame(beta = comp_obj$beta,
                           pcor = comp_obj$pcor) 
  n_samples <- length(comp_obj$beta_ref_a)
  
  if(isTRUE(combine_posteriors)){
     overlap_df$beta_ref <- c(
                          comp_obj$beta_ref_a[sample(1:n_samples, n_samples/2)], 
                          comp_obj$beta_ref_b[sample(1:n_samples, n_samples/2)])
     overlap_df$pcor_ref <- c(
                          comp_obj$pcor_ref_a[sample(1:n_samples, n_samples/2)], 
                          comp_obj$pcor_ref_b[sample(1:n_samples, n_samples/2)])
     
  } else {
    stop("Comparing against two distributions is not implemented yet.")
  }
  
  
  # Quantify the overlap
  erb <- equiv_range_beta * (nvar * nvar)
  erp <- equiv_range_pcor * ((nvar * nvar)/2 - nvar/2)
  
  res_df <- overlap_df %>%
    dplyr::mutate(
           beta = beta - erb,
           pcor = pcor - erp) %>%
    dplyr::summarize(
      larger_beta = mean(beta > beta_ref),
      larger_pcor = mean(pcor > pcor_ref)
    )
  
  return(res_df)
  
}
```



## Analyze results on the server
```{r}
file_list <- list.files(path = here::here("data/revision1/compare_sim_res"))

time_before_within_eval <- Sys.time()
ncores = 50
cl = makeCluster(ncores)
registerDoParallel(cl)
clusterExport(cl, c("compare_posterior_mean"))
clusterEvalQ(cl, library(tidyverse))
l_comp_res <- list()
l_comp_res <- foreach(i = 1:length(file_list)) %dopar% {
  comp_res <- readRDS(here::here(paste0("data/revision1/compare_sim_res/",file_list[i])))
  
  ## Obtain information from filename
  file_str <- file_list[i]
  file_str_split <- strsplit(file_str, split = "_")
  # for non-narrow condition
  if(length(file_str_split[[1]]) == 5){
  dgp_it <- file_str_split[[1]][2]
  change_it <- file_str_split[[1]][3]
  tp_it <- file_str_split[[1]][4]
  comp_it <- file_str_split[[1]][5]
  # delete file ending 
  comp_it <- gsub("\\..*", "", comp_it)
  }
  # for narrow condition
  if(length(file_str_split[[1]]) == 6){
  dgp_it <- paste(file_str_split[[1]][2], file_str_split[[1]][3], sep = "_")
  change_it <- file_str_split[[1]][4]
  tp_it <- file_str_split[[1]][5]
  comp_it <- file_str_split[[1]][6]
  # delete file ending 
  comp_it <- gsub("\\..*", "", comp_it)
  }

  ## Evaluation
  # Loop over all comparisons
  eval_res <- list()
  eval_res <- lapply(comp_res, function(x){
    
    res <- compare_posterior_mean(x, 
                                  equiv_range_beta = 0,
                                  equiv_range_pcor = 0,
                                  combine_posteriors = TRUE,
                                  nvar = 6)
    
    res$dgp <- dgp_it
    res$change <- change_it
    res$tp <- tp_it
    res$comp <- comp_it

    return(res)
  })
  
  
  ## Output
  # Combine all results into dataframe
  df_eval_res <- do.call(rbind.data.frame, eval_res)
  print(paste0("File ", i, " done!"))
  
  # Save output
  saveRDS(df_eval_res, file = here::here(paste0("data/revision1/postmean_res/postmean_res_",dgp_it, "_",change_it,"_", tp_it, "_",comp_it, ".RDS")))
  
}
stopCluster(cl)

time_after_within_eval <- Sys.time() - time_before_within_eval

```

Read in results again, they were saved as individual files. 
```{r}
# For wide priors
file_list <- list.files(path = here("data/revision1/postmean_res"), full.names = TRUE)
file_list_w <- file_list[-grep("_narrow_", file_list)]
l_comp_res_w <- lapply(file_list_w, readRDS)
df_comp_res_w <- do.call(rbind, l_comp_res_w)


# For narrow priors
file_list <- list.files(path = here("data/revision1/postmean_res"), full.names = TRUE)
file_list_n <- file_list[grep("_narrow_", file_list)]
l_comp_res_n <- lapply(file_list_n, readRDS)
df_comp_res_n <- do.call(rbind, l_comp_res_n)


# Combine both 
df_comp_res_w$prior <- rep("wide", nrow(df_comp_res_w))
df_comp_res_n$prior <- rep("narrow", nrow(df_comp_res_n))

df_comp_res <- rbind(df_comp_res_w, df_comp_res_n)

# write_rds(df_comp_res, here::here("output/revision1/df_postmean_res.RDS"))
df_postmean_res <- read_rds(here::here("output/revision1/df_postmean_res.RDS"))

```


# Analyze results

## Proportions
```{r}
change_names <- c("change1.4" = paste("Largest", "\u00D7", "1.4"),
                  "change1.6" = paste("Largest", "\u00D7", "1.6"),
                  "const0.05" = paste("All", "\u00b1", "0.05"),
                  "const0.1" = paste("All", "\u00b1", "0.10"),
                  "const0.15" = paste("All", "\u00b1", "0.15"),
                  "permute" = "Permute",
                  "truegraph" = "Same DGP"
)

graph_names <- c("Empirical\nSparse" = "graph3",
                 "Simulated\nChain" = "graph4",
                 "Simulated\nNonsparse" = "graph5")

norm_names <- c("frob" = "Frobenius",
                "l1" = "\u2113[1]",
                "maxdiff" = "Maxdiff")

tp_levels <- c("50" = "1", "100" = "2", "200" = "3", "400" = "4", "1000" = "5")

# plotting linetypes
cond_lty <- set_names(c(1,2),
                      c("narrow", "wide"))

df_postmean <- df_postmean_res %>% 
  mutate(tp = as.factor(tp)) %>% 
      mutate(tp = forcats::fct_relevel(tp, "50", "100", "200", "400", "1000")) %>% 
      mutate(dgp = gsub("narrow_", "", dgp)) %>%
      dplyr::mutate(dgp = fct_recode(as_factor(as.character(dgp)), !!!graph_names)) %>% 
      dplyr::mutate(change = case_match(
            change,
                  "change1.4" ~ paste("Largest", "\u00D7", "1.4"),
                  "change1.6" ~ paste("Largest", "\u00D7", "1.6"),
                  "const0.05" ~ paste("All", "\u00b1", "0.05"),
                  "const0.1" ~ paste("All", "\u00b1", "0.10"),
                  "const0.15" ~ paste("All", "\u00b1", "0.15"),
                  "permute134256" ~ "Permute",
                  "truegraph" ~ "Same DGP"
          )) %>% 
          dplyr::mutate(change = as.factor(change)) %>% 
          dplyr::mutate(change = forcats::fct_relevel(change, 
                                                      "Same DGP",
                                                      "Largest × 1.4", 
                                                      "Largest × 1.6",
                                                      "All ± 0.05",
                                                      "All ± 0.10",
                                                      "All ± 0.15",
                                                      "Permute")) %>% 
  pivot_longer(cols = c(larger_beta, larger_pcor), 
               names_to = "matrix", 
               values_to = "larger") %>%
  mutate(matrix = gsub("larger_", "", matrix))

```


Visualize results
```{r}
plot_postmean_comp <- df_postmean %>% 
  ggplot(aes(x = tp, y = larger, color = prior)) + 
  geom_boxplot() + 
  theme_compare()  +
  facet_nested(comp + change ~ matrix + dgp) +
  ggokabeito::scale_color_okabe_ito(order = c(5, 1:8))+
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, length(tp_levels), 1))+
  theme(panel.grid.major.x = element_blank())

ggsave(here::here("figures/revision1/plot_postmean_comp.pdf"), plot_postmean_comp, width = 20, height = 15)

```


## Decisions

```{r}
plot_postmean_dec99 <- df_postmean %>% 
  mutate(dec95 = if_else(larger >= 0.95, 1, 0),
         dec99 = if_else(larger >= 0.99, 1, 0)) %>% 
  group_by(dgp, change, tp, comp, prior, matrix) %>%
  summarize(dec95 = mean(dec95),
            dec99 = mean(dec99)) %>%
  ggplot(aes(x = tp, y = dec99, color = prior)) +
  geom_point()+
  theme_compare()  +
  facet_nested(comp + change ~ matrix + dgp) +
  ggokabeito::scale_color_okabe_ito(order = c(5, 1:8))+
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, length(tp_levels), 1))+
  theme(panel.grid.major.x = element_blank())

ggsave(here::here("figures/revision1/plot_postmean_dec99.pdf"), plot_postmean_dec99, width = 20, height = 15)
  
```





